---
title: "Untitled"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo = FALSE,warning = FALSE, message=FALSE)

library(tidyverse)
library(readxl)
library(readr)
library(pacman)
library(shadowtext)
library(ggrepel)
library(sf)
library("rnaturalearth")
library("rnaturalearthdata")
library(viridis)
library(metR)
library(ggnewscale)
library(maps)
library(RColorBrewer)
library(forcats)
  library("rnaturalearthdata")
  #library(raster)
  library("sf")
  library(stringr)
  library(cowplot)
  library(dbplyr)
  library(dplyr)
  library(grid) # for unit
  library(gridExtra) # for grid.arrange
  libs <- c("rgdal", "maptools", "gridExtra")
  library(knitr)
  library(kableExtra)
  library(shadowtext)
  library(ggrepel)
    library(arrow)
  set.seed(42)
  lapply(libs, require, character.only = TRUE)
  library(ggExtra)
  library(scales)
  library(waterfalls)
library(directlabels)
library(forcats)
  library(slider)
  library(gtools)
library(purrr)

# install.packages('devtools')
#devtools::install_github('bbc/bbplot')
library('bbplot')
  
#install.packages("ggmagnify", repos = c("https://hughjonesd.r-universe.dev", 
#                 "https://cloud.r-project.org"))

pacman::p_load('dplyr', 'tidyr', 'gapminder',
               'ggplot2',  'ggalt',
               'forcats', 'R.utils', 'png', 
               'grid', 'ggpubr', 'scales',
               'bbplot', 'ggalluvial','ggforce','ggmagnify','RNetCDF')


SAVE_ici<-TRUE
SAVE_ici_bis<-FALSE

```

# chargement données

```{r load data}

exposure_tn_65_plus_abs<-read_delim("./data/exposure_tn_classes_65+_abs.csv",delim=";") %>% 
  rename ("temperature" = "...1") 

exposure_tn_65_plus_new <- exposure_tn_65_plus_abs %>% 
  pivot_longer(cols=-c(temperature)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP","AGE")) %>% 
  filter(!grepl("REP",AGE)) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  separate_wider_position(AGE,widths = c( 3,AGE = 2))

exposure_tropnight_65_plus_abs<-read_delim("./data/exposure_tropnight_dates_65+_abs.csv",delim=";") %>% 
  rename ("temperature" = "...1") %>% 
  mutate(date=as.Date(temperature, format = "%Y-%m-%d")) %>% 
  dplyr::select(-temperature)

exposure_tropnight_65_plus_abs_new <- exposure_tropnight_65_plus_abs %>% 
  pivot_longer(cols=-c(date)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP","AGE")) %>% 
  filter(!grepl("REP",AGE)) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  separate_wider_position(AGE,widths = c( 3,AGE = 2))


exposure_tropnight_classe_65_plus<-read_delim("./data/exposure_tropnight_classes_65+_abs.csv",delim=";") %>% 
  rename ("temperature" = "...1")

exposure_tropnight_classe_65_plus_new <- exposure_tropnight_classe_65_plus %>% 
  pivot_longer(cols=-c(temperature)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP","AGE")) %>% 
  filter(!grepl("REP",AGE)) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  separate_wider_position(AGE,widths = c( 3,AGE = 2))

exposure_tropnight_classe_65_minus<-read_delim("./data/exposure_tropnight_classes_65-_abs.csv",delim=";") %>% 
  rename ("temperature" = "...1")


exposure_tn_p90_classes_65_plus_abs<-read_delim("./data/exposure_tn_p90_classes_65+_abs.csv",delim=";") %>% 
  rename ("temperature" = "...1") 

exposure_tn_p90_classes_65_plus_new <- exposure_tn_p90_classes_65_plus_abs %>% 
  pivot_longer(cols=-c(temperature)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP","AGE")) %>% 
  filter(!grepl("REP",AGE)) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  separate_wider_position(AGE,widths = c( 3,AGE = 2))


final_data <- read_parquet("./data/final_data.parquet")

final_data_consecutive <- read_parquet("./data/final_data_consecutive.parquet")

draw_ici <- TRUE
```

# histogramme
## cumulative graph
```{r}


# Reshape to long format
df_long <- final_data %>%
  filter(year %in% c(2017,2018,2019,2020,2022)) %>% 
  dplyr::select(`65+_90`,`65+_18`,nb_nuit_trop_C,nb_nuit_trop_D,year,INSEE_COM) %>% 
  rename("pop_1990" = "65+_90",
         "pop_2018" = "65+_18",
         "hot_days_1990" = "nb_nuit_trop_C",
         "hot_days_2018" = "nb_nuit_trop_D") %>% 
  pivot_longer(
    cols = c(pop_1990, pop_2018, hot_days_1990, hot_days_2018),
    names_to = c(".value", "scenario"),
    names_pattern = "(.+)_(1990|2018)"
  ) %>%
  rename(population = pop, hot_days = hot_days) %>%
  mutate(scenario = paste("If population and land use\nwere as in", scenario))

# For each hot_days threshold, compute cumulative population exceeding it
hot_day_vals <- sort(unique(df_long$hot_days))

cumulative_df <- df_long %>%
  group_by(scenario,year) %>%
  reframe(
    hot_days_threshold = hot_day_vals,
    cum_pop = sapply(hot_day_vals, function(x) {
      sum(population[hot_days >= x])
    })
  )

cumulative_df %>% filter(hot_days_threshold ==1)
cumulative_df %>% filter(hot_days_threshold ==11) %>% 
  pivot_wider(names_from = scenario, values_from = cum_pop) %>% 
  mutate(ratio = `If population and land use\nwere as in 2018`/`If population and land use\nwere as in 1990`)

# Plot
p <- ggplot(cumulative_df, aes(x = hot_days_threshold, y = cum_pop / 1e6, color = scenario, fill = scenario)) +
  geom_step(linewidth = 1) +
  labs(
    title = "Cumulative population aged  65 years and over\nexposed to at least X tropical nights",
    x = "Number of tropical nights (threshold)",
    y = "Cumulative population (millions)",
    color = "",
    fill = ""
  ) +
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  facet_wrap(~ year) +
  bbc_style()+
  theme(
    axis.ticks.x = element_line(colour = "#333333"),
    axis.ticks.length =  unit(0.26, "cm"),
    legend.position = "top", 
    legend.justification = "left",
    #axis.ticks.x = element_line(colour = "#333333"), 
    #axis.ticks.length =  unit(0.26, "cm"),
    axis.title = element_text(angle=0,size=16),
    panel.grid.major.x = element_line(color="#cbcbcb"), 
  )
p
  # theme_minimal(base_size = 18) +
  # theme(legend.position = "top")

ggsave(paste0("./outputs/par_canicule/cumulative.png"),plot=p,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```


# waterfall tn 65 +

## AGE

### ordre 1

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_AGE = LULC90_POP90_AGE18 - LULC90_POP90_AGE90,
    evol_POP = LULC90_POP18_AGE18 - LULC90_POP90_AGE18,
    evol_LU = LULC18_POP18_AGE18 - LULC90_POP18_AGE18) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre1.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

### ordre 2

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_LU = LULC18_POP90_AGE90 - LULC90_POP90_AGE90,
    evol_AGE = LULC18_POP90_AGE18 - LULC18_POP90_AGE90,
    evol_POP = LULC18_POP18_AGE18 - LULC18_POP90_AGE18,
    ) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","UHI variation","change in\npopulation age", "change in\npopulation location"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre2.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

### ordre 3

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_LU = LULC18_POP90_AGE90 - LULC90_POP90_AGE90,
    evol_POP = LULC18_POP18_AGE90 - LULC18_POP90_AGE90,
    evol_AGE = LULC18_POP18_AGE18 - LULC18_POP18_AGE90,
    ) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","UHI variation", "change in\npopulation location","change in\npopulation age"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre3.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

### ordre 4

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_POP = LULC90_POP18_AGE90 - LULC90_POP90_AGE90,
    evol_AGE = LULC90_POP18_AGE18 - LULC90_POP18_AGE90,
    evol_LU = LULC18_POP18_AGE18 - LULC90_POP18_AGE18) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre4.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

### ordre 5

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_POP = LULC90_POP18_AGE90 - LULC90_POP90_AGE90,
    evol_LU = LULC18_POP18_AGE90 - LULC90_POP18_AGE90,
    evol_AGE = LULC18_POP18_AGE18 - LULC18_POP18_AGE90) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation location" ,"UHI variation","change in\npopulation age"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre5.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

### ordre 6

```{r}

tmp <- exposure_tn_65_plus_abs %>% 
  mutate(
    evol_AGE = LULC90_POP90_AGE18 - LULC90_POP90_AGE90,
    evol_LU = LULC18_POP90_AGE18 - LULC90_POP90_AGE18,
    evol_POP = LULC18_POP18_AGE18 - LULC18_POP90_AGE18) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(-c(temperature))%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age" ,"UHI variation","change in\npopulation location"))) %>% 
  filter(temperature=="[16;17[") %>% 
  dplyr::select(-c(temperature)) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

ggsave(paste0("./outputs/tn_65_age/ordre6.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

## evolution en fonction du temps
### people*number moyenne glissante tropical nights

```{r}
window_size=15


df <- exposure_tropnight_65_plus_abs_new %>% 
    filter(AGE == POP) %>% 
    dplyr::select(-AGE) %>% 
  mutate(year = year(date)) %>%
  arrange(year) %>%
  group_by(year,LULC,POP ) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value2 = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size)
  #slice(c(1, n())) %>%  #juste premiere et derniere ligne

df %>% ggplot(aes(x=year,group=interaction(LULC,POP)))+
  geom_point(aes(y=value))+
  geom_line(aes(y=value2))




p<-df %>%   
  ggplot(aes(x=year,y=value,group=interaction(LULC,POP),color=interaction(LULC,POP)))+
  geom_line()+
  bbc_style()+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")


p
  

```
### nombre par an 

```{r}
window_size=15


df <- trop_commune_year2 %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value2 = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index_chr(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  ungroup() 

df %>% ggplot(aes(x=window,group=interaction(LULC,POP)))+
  geom_point(aes(y=value))+
  geom_line(aes(y=value2))




p<-df %>%   
  ggplot(aes(x=window,y=value2,group=interaction(LULC,POP),color=interaction(LULC,POP)))+
  geom_line()+
  bbc_style()+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")


p
  

```



### tropical nights avec evol climat

```{r}

window_size=20

tmp <- exposure_tropnight_65_plus_abs %>%
  mutate(year = year(date)) %>%
  arrange(year) %>%
  group_by(year) %>%
  summarise(
    LULC90_POP90_AGE90 = sum(LULC90_POP90_AGE90),
    LULC18_POP18_AGE18 = sum(LULC18_POP18_AGE18),
    LULC90_POP18_AGE18 = sum(LULC90_POP18_AGE18),
    LULC90_POP90_AGE18 = sum(LULC90_POP90_AGE18),
    `LULC18+POP90` = sum(`LULC18+POP90`),
    # LULC90_POP90_AGE90 = mean(LULC90_POP90_AGE90),
    # LULC18_POP18_AGE18 = mean(LULC18_POP18_AGE18),
    # LULC90_POP18_AGE18 = mean(LULC90_POP18_AGE18),
    # LULC90_POP90_AGE18 = mean(LULC90_POP90_AGE18),
    # `LULC18+POP90` = mean(`LULC18+POP90`), 
    .groups = "drop") %>%
  mutate(
    LULC90_POP90_AGE90 = slide_index_dbl(LULC90_POP90_AGE90,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    LULC90_POP18_AGE18 = slide_index_dbl(LULC90_POP18_AGE18,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    LULC90_POP90_AGE18 = slide_index_dbl(LULC90_POP90_AGE18,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    `LULC18+POP90` = slide_index_dbl(`LULC18+POP90`,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    LULC18_POP18_AGE18 = slide_index_dbl(LULC18_POP18_AGE18,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
    
        # number of years in window
    n_years = slide_index_int(
      `LULC18+POP90`,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  ) %>% 
  filter(n_years == window_size)


tmp2 <- tmp %>%   #slice(c(1, n())) %>%  #juste premiere et derniere ligne
  filter(year %in% c(2000+window_size-1, 2022)) %>% 
  mutate(period = case_when(
    year == 2000+window_size-1 ~"beginning",
    year == 2022 ~"end"
  ))%>% 
  dplyr::select(-c(year,window,n_years)) %>% 
  pivot_longer(-c(period))%>% 
  mutate(name=paste0(name,"_",period)) %>% 
  dplyr::select (-period) %>% 
  pivot_wider()%>% 
  mutate(
    evol_AGE = `LULC90+POP90age18_beginning` - `LULC90+POP90_beginning`,
    evol_POP = `LULC90+POP18_beginning` - `LULC90+POP90age18_beginning`,
    evol_LU = `LULC18+POP18_beginning` - `LULC90+POP18_beginning`,
    evol_climat = `LULC18+POP18_end` - `LULC18+POP18_beginning`)%>% 
  dplyr::select(evol_climat,evol_LU,evol_POP,evol_AGE,`LULC90+POP90_beginning`) %>% 
    rename("1990"="LULC90+POP90_beginning",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP",
         "change in\nclimate" = "evol_climat")  %>% 
  pivot_longer(cols = everything())%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation","change in\nclimate"))) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp2$name,
             values = tmp2$value/1000,
             rect_text_labels=round(tmp2$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=1500,
             calc_total=TRUE,
             total_axis_text="2022",
             total_rect_text=round(sum(tmp2$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Population*number of tropical nights",
          subtitle = "thousands, sum per year, average for 20 years =, people 65+")

p

ggsave(paste0("./outputs/tropical_nights_65.png"),plot=p,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```

### tropical nights sans evol climat

```{r}
exposure_tropnight_65_plus_abs %>% 
  group_by(year = lubridate::floor_date(date, unit="year")) %>%
    summarize(nombre = n())%>% 
  ggplot(aes(y=nombre,x=year))+
  geom_point()+
  geom_smooth()

tmp <- exposure_tropnight_65_plus_abs %>% 
  #group_by(year = lubridate::floor_date(date, unit="year")) %>%
  summarise(
    LULC90_POP90_AGE90 = sum(LULC90_POP90_AGE90),
    LULC18_POP18_AGE18 = sum(LULC18_POP18_AGE18),
    LULC90_POP18_AGE18 = sum(LULC90_POP18_AGE18),
    LULC90_POP90_AGE18 = sum(LULC90_POP90_AGE18),
    `LULC18+POP90` = sum(`LULC18+POP90`),
  ) %>% 
  mutate(
    evol_AGE = LULC90_POP90_AGE18 - LULC90_POP90_AGE90,
    evol_POP = LULC90_POP18_AGE18 - LULC90_POP90_AGE18,
    evol_LU = LULC18_POP18_AGE18 - LULC90_POP18_AGE18)%>% 
  dplyr::select(evol_LU,evol_POP,evol_AGE,LULC90_POP90_AGE90) %>% 
    rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(cols = everything())%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation"))) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

p

ggsave(paste0("./outputs/tropical_nights_65.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```


## 12 classes tropical nights

```{r}
tmp <- exposure_tropnight_classe_65_plus %>% 
  mutate(
    evol_AGE = `LULC90+POP90rep18` - LULC90_POP90_AGE90,
    evol_POP = LULC90_POP18_AGE18 - `LULC90+POP90rep18`,
    evol_LU = LULC18_POP18_AGE18 - LULC90_POP18_AGE18) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  #filter(temperature  %in% c("[12;14[","[10;12[")) %>% 
  filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  summarise(across(everything(), ~ sum(.x, na.rm = TRUE))) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(everything())%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation"))) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Number of people exposed\nto more than 12 tropical nights",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

p

ggsave(paste0("./outputs/tropical_nights_12.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```

## 6 classes tropical nights

### ordre 1

```{r}
tmp <- exposure_tropnight_classe_65_plus %>% 
  mutate(
    evol_AGE = `LULC90+POP90rep18` - LULC90_POP90_AGE90,
    evol_POP = LULC90_POP18_AGE18 - `LULC90+POP90rep18`,
    evol_LU = LULC18_POP18_AGE18 - LULC90_POP18_AGE18) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  #filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  summarise(across(everything(), ~ sum(.x, na.rm = TRUE))) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(everything())%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age", "change in\npopulation location","UHI variation"))) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Number of people exposed\nto more than 6 tropical nights",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

p

ggsave(paste0("./outputs/tropical_nights_6.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```

### ordre 2

```{r}
tmp <- exposure_tropnight_classe_65_plus %>% 
  mutate(
    evol_AGE = `LULC90+POP90rep18` - LULC90_POP90_AGE90,
    evol_LU = `LULC18+POP90rep18` - `LULC90+POP90rep18`,
    evol_POP = LULC18_POP18_AGE18 - `LULC18+POP90rep18`,
    ) %>% 
  dplyr::select(temperature,evol_LU,evol_POP,,evol_AGE,LULC90_POP90_AGE90) %>% 
  filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  #filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  summarise(across(everything(), ~ sum(.x, na.rm = TRUE))) %>% 
  rename("1990"="LULC90_POP90_AGE90",
         "UHI variation" = "evol_LU",
         "change in\npopulation age" = "evol_AGE",
         "change in\npopulation location" ="evol_POP")  %>% 
  pivot_longer(everything())%>% 
  mutate(ordre=factor(name,levels = c("1990","change in\npopulation age","UHI variation", "change in\npopulation location"))) %>% 
  arrange(ordre)

p<-waterfall(labels = tmp$name,
             values = tmp$value/1000,
             rect_text_labels=round(tmp$value/1000),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=25,
             calc_total=TRUE,
             total_axis_text="2018",
             total_rect_text=round(sum(tmp$value/1000))
)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ggtitle("Number of people exposed\nto more than 6 tropical nights",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")

p

ggsave(paste0("./outputs/tropical_nights_6_ordre2.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```

## essai waterfall main

```{r}

df <- exposure_tn_65_plus_new %>% 
  filter(temperature == "[16;17[")

debut <- df %>% 
  filter(LULC == 90,
         POP == 90,
         AGE == 90) %>% 
  dplyr::select(value) %>% 
  rename("contribution" = "value") %>% 
  mutate(step = "1990")

fin <- df %>% 
  filter(LULC == 18,
         POP == 18,
         AGE == 18) %>% 
  dplyr::select(value) %>% 
  rename("contribution" = "value") %>% 
  mutate(step = "2018") %>% 
  mutate(contribution = -contribution)

get_value <- function(state) {
  df %>%
    filter(
      LULC == state["LULC"],
      AGE  == state["AGE"],
      POP  == state["POP"]
    ) %>%
    pull(value)
}

# =========================
# ALL PERMUTATIONS
# =========================
vars <- c("LULC", "AGE", "POP")
perms <- permutations(3, 3, vars)

# =========================
# SINGLE PATH DECOMPOSITION
# =========================
decompose_path <- function(order) {
  
  state <- c(LULC = 90, AGE = 90, POP = 90)
  prev <- get_value(state)
  
  out <- list()
  
  for (i in 1:3) {
    
    var <- order[i]
    state[var] <- 18
    
    new <- get_value(state)
    
    out[[i]] <- data.frame(
      permutation = paste(order, collapse = "→"),
      step = var,
      contribution = new - prev
    )
    
    prev <- new
  }
  
  bind_rows(out)
}

# =========================
# ALL PERMUTATION CONTRIBUTIONS (DATAFRAME REQUESTED)
# =========================
perm_df <- bind_rows(lapply(1:nrow(perms), function(i) {
  decompose_path(perms[i, ])
}))


perm_df2 <- debut %>% 
  bind_rows(perm_df %>%   filter(permutation  == "AGE→LULC→POP") %>% dplyr::select(-permutation)) %>% 
  bind_rows(fin)

# 
# df <- read_delim("./permutation_contributions.csv",delim=",") %>% 
#   filter(permutation  == "AGE→LULC→POP")

levels <- perm_df2$step

data1 <- perm_df2  %>%
    mutate(step = factor(step, levels = levels),
        ymin = round(cumsum(contribution), 3),
        ymax = lag(cumsum(contribution), default = 0),
        xmin = c(head(step, -1), NA),
        xmax = c(tail(step, -1), NA),
        Impact = ifelse(step %in% c(as.character(perm_df2$step[1]), as.character(perm_df2$step[nrow(perm_df2)])),"Budget",
                        ifelse(contribution > 0, "Increase", "Decrease")
           )) %>% 
  mutate(ymin=ymin/1000,
         ymax = ymax /1000) %>% 
  mutate(step2 = as.factor(case_when(
        step == "LULC" ~ "UHI variation",
        step == "AGE" ~ "change in\npopulation age",
        step == "POP" ~ "change in\npopulation location",
        TRUE ~ step)))

w <- 0.7  #use to set width of bars

put_rect_text_outside_when_value_below = 27

g <- data1 %>% 
  mutate(label_ici = round(ymin-ymax)) %>% 
  mutate(label_ici = if_else(step == "2018",-label_ici,label_ici)) %>% 
  ggplot() +
    geom_rect(aes(xmin = as.integer(step) - w/2,
                  xmax = as.integer(step) + w/2, ymin = ymin, ymax = ymax,
                  fill = Impact), colour = "black") +
    scale_x_discrete(labels =data1$step2 ,limits = levels) +
    scale_fill_manual(values = (c("Decrease" = "#FAAB18",  "Increase" = "#1380A1" , "Budget" = "black"))) +
  geom_segment(data = data1[1:(nrow(data1) -1),],
               aes(x = xmin,
                   xend = xmax,
                   y = ymin,
                   yend = ymin),
               linetype="dashed")+
  geom_text(aes(x = as.integer(step) ,
                y = if_else(abs(ymin-ymax)> put_rect_text_outside_when_value_below,
                            ymin /2 + ymax /2,
                            ymax - put_rect_text_outside_when_value_below), 
                label = label_ici,
                color = abs(ymin-ymax)< put_rect_text_outside_when_value_below #(Impact != "Budget")
                                ),
            size=7)+
  scale_color_manual(values = c("white","black"))+
  bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Change in population exposed to heat",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")+
  geom_hline(yintercept =0)
g

ggsave(paste0("./outputs/tn_65_age/ordre0.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

```

### fonction waterfall

```{r}


draw_waterfall <- function(shapley_df = shapley_df,df = df,vars = c("LULC", "AGE", "POP"),start_val = 90, end_val = 18,title_ici ="Change in population exposed to heat",subtitle_ici = "Thousands of people, age 65+, Tn > 15°C",put_rect_text_outside_when_value_below = 27)
{
  # =========================
# VALUE FUNCTION
# =========================

get_value <- function(state) {
  
  conds <- Map(function(var) {
    df[[var]] == state[[var]]
  }, vars)
  
  rows <- Reduce(`&`, conds)
  
  val <- df$value[rows]
  
  if (length(val) != 1) {
    stop("State not uniquely matched")
  }
  
  return(val)
}

# =========================
# ALL PERMUTATIONS
# =========================
k <- length(vars)

# =========================
# START / END VALUES
# =========================
v_start <- get_value(setNames(rep(start_val, k), vars))
v_end   <- -get_value(setNames(rep(end_val, k), vars))


wf <- data.frame(
  step = c("If population\nand land use\nas in 1990", shapley_df$variable, "If population\nand land use\nas in 2018"),
  value = c(v_start, shapley_df$shapley, v_end),
  type = c("total", rep("change", k), "total")
)


levels <- wf$step

# =========================
# SETUP for graph
# =========================
data1 <- wf  %>%
    mutate(step = factor(step, levels = levels),
        ymin = round(cumsum(value),  length(vars)),
        ymax = lag(cumsum(value), default = 0),
        xmin = c(head(step, -1), NA),
        xmax = c(tail(step, -1), NA),
        Impact = ifelse(step %in% c(as.character(wf$step[1]), as.character(wf$step[nrow(wf)])),"Budget",
                        ifelse(value > 0, "Increase", "Decrease")
           )) %>% 
  mutate(ymin=ymin/1000,
         ymax = ymax /1000) %>% 
  mutate(step2 = as.factor(case_when(
          # step == "LULC" ~ "impact of\nland-use change\non urban climate",
          # step == "year" ~ "climate change",
          # step == "AGE" ~ "change in the ratio\nof people aged 65+\nin the population",
          # step == "POP" ~ "change in the\nlocation of people\naged 65+ within\nthe region",
          # step == "REP" ~ "global population\nincrease in the\nregion",
          # step == "REP_age" ~ "change in the ratio\nof people aged 65+\nin the population",
          step == "LULC" ~ "Land-use change\n(urban\nclimate)",
          step == "year" ~ "Climate change",
          step == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
          step == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
          step == "REP" ~ "Total population\nincrease",
          step == "REP_age" ~ "Population\nage structure",
        TRUE ~ step)))

# =========================
# WATERFALL PLOT
# =========================

w <- 0.7  #use to set width of bars

g <- data1 %>% 
  mutate(label_ici = round(ymin-ymax)) %>% 
  mutate(label_ici = if_else(step == "If population\nand land use\nas in 2018",-label_ici,label_ici)) %>% 
  ggplot() +
    geom_rect(aes(xmin = as.integer(step) - w/2,
                  xmax = as.integer(step) + w/2, ymin = ymin, ymax = ymax,
                  fill = Impact), colour = "black") +
    scale_x_discrete(labels =data1$step2 ,limits = levels) +
    scale_fill_manual(values = (c("Decrease" = "#FAAB18",  "Increase" = "#1380A1" , "Budget" = "black"))) +
  geom_segment(data = data1[1:(nrow(data1) -1),],
               aes(x = xmin,
                   xend = xmax,
                   y = ymin,
                   yend = ymin),
               linetype="dashed")+
  geom_text(aes(x = as.integer(step) ,
                y = if_else(abs(ymin-ymax)> put_rect_text_outside_when_value_below,
                            ymin /2 + ymax /2,
                           ymin /2 + ymax /2- put_rect_text_outside_when_value_below
                            ), 
                label = label_ici,
                color = abs(ymin-ymax)< put_rect_text_outside_when_value_below #(Impact != "Budget")
                                ),
            size=7)+
  scale_color_manual(values = c("white","black"))+
  bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle(title_ici,
          subtitle = subtitle_ici)+
  geom_hline(yintercept =0)

return(g)

#write.csv(perm_df, "permutation_contributions.csv", row.names = FALSE)
#write.csv(shapley_df, "shapley_values.csv", row.names = FALSE)
}

```



### compute permut

```{r}
compute_permut <- function(df,vars = c("LULC", "AGE", "POP"),start_val = 90, end_val = 18)
{
  # =========================
# VALUE FUNCTION
# =========================

get_value <- function(state) {
  
  conds <- Map(function(var) {
    df[[var]] == state[[var]]
  }, vars)
  
  rows <- Reduce(`&`, conds)
  
  val <- df$value[rows]
  
  if (length(val) != 1) {
    stop("State not uniquely matched")
  }
  
  return(val)
}

# =========================
# ALL PERMUTATIONS
# =========================
k <- length(vars)
perms <- permutations(k, k, vars)

# =========================
# PATH DECOMPOSITION
# =========================
decompose_path <- function(order) {
  
  state <- setNames(rep(start_val, k), vars)
  prev <- get_value(state)
  
  out <- list()
  
  for (i in seq_along(order)) {
    
    var <- order[i]
    state[var] <- end_val
    
    new <- get_value(state)
    
    out[[i]] <- data.frame(
      permutation = paste(order, collapse = "→"),
      variable = var,
      contribution = new - prev
    )
    
    prev <- new
  }
  
  bind_rows(out)
}

# =========================
# ALL PERMUTATION CONTRIBUTIONS
# =========================
perm_df <- bind_rows(lapply(1:nrow(perms), function(i) {
  decompose_path(perms[i, ])
}))


perm_df <- map_dfr(1:nrow(perms), ~ decompose_path(perms[.x, ]))


return(perm_df)

#write.csv(perm_df, "permutation_contributions.csv", row.names = FALSE)
#write.csv(shapley_df, "shapley_values.csv", row.names = FALSE)
}
```

### tn

#### 3 classes

```{r}
df <- exposure_tn_65_plus_new %>% 
  filter(temperature == "[16;17[") %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1 149 599
#65+ 2018: 1 812 696
# pop totale Idf 1990: 10 644 665
# pop totale Idf 2018: 12 213 447



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/1812696*1149599,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*1812696/1149599,value))

df_tmp <- rbind(df2,df3)


perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18)
g

perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable,\nfor all permutations",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")+
  geom_hline(yintercept =0)
```

#### 4 classes

```{r}
df <- exposure_tn_65_plus_new %>% 
  filter(temperature == "[16;17[") %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1149599
#65+ 2018: 1812696
# pop totale Idf 1990: 10644665
# pop totale Idf 2018: 12213447

ratio_65_1990 = 1149599/10644665  
ratio_65_2018 = 1812696/12213447  

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","REP_age" ,"POP" ,"LULC","value")

perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18)
g

perm_df %>% 
  ggplot(aes(x=variable,y=contribution))+
  geom_jitter()
```

### 12 tropical night classes
#### 3 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  filter(temperature == "[12;14[") %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1 149 599
#65+ 2018: 1 812 696
# pop totale Idf 1990: 10 644 665
# pop totale Idf 2018: 12 213 447



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/1812696*1149599,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*1812696/1149599,value))

df_tmp <- rbind(df2,df3)


perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed\nto more than 12 tropical nights",  subtitle = "Thousands of people, age 65+")
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population\nnumber",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=5)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n12 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_3_12 trop_nights.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_3_12 trop_nights.png"),plot=h,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```




#### 4 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  filter(temperature == "[12;14[") %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

ratio_65_1990 = 1149599/10644665 
ratio_65_2018 = 1812696/12213447 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","REP_age" ,"POP" ,"LULC","value")

perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n12 tropical nights",  subtitle = "Thousands of people, age 65+, Tn > 15°C",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n12 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_4_12 trop_nights.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_4_12 trop_nights.png"),plot=h,
       width = 2666/280,
       height= 1875/280,
       unit="in")

```

### 10 tropical night classes

#### 3 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  #filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  filter(temperature  %in% c("[12;14[","[10;12["))%>% 
  #filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  group_by(LULC,POP,AGE ) %>% 
  summarise(value=sum(value)) %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1 149 599
#65+ 2018: 1 812 696
# pop totale Idf 1990: 10 644 665
# pop totale Idf 2018: 12 213 447



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/1812696*1149599,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*1812696/1149599,value))

df_tmp <- rbind(df2,df3)


perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed\nto more than 10 tropical nights",  subtitle = "Thousands of people, age 65+")
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population\nnumber",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=5)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_3_10 trop_nights.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_3_10 trop_nights.png"),plot=h,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```



#### 4 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  #filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  filter(temperature  %in% c("[12;14[","[10;12[")) %>% 
  dplyr::select(-temperature) %>% 
  group_by(LULC,POP,AGE ) %>% 
  summarise(value=sum(value)) %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

ratio_65_1990 = 1149599/10644665 
ratio_65_2018 = 1812696/12213447 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","REP_age" ,"POP" ,"LULC","value")

perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+C",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_4_10 trop_nights.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_4_10 trop_nights.png"),plot=h,
       width = 2666/280,
       height= 1875/280,
       unit="in")

```

#### 5 classes

```{r}
window_size=15

df <- final_data %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2014,2022))


ratio_65_1990 = 1149599/10644665 
ratio_65_2018 = 1812696/12213447 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","REP_age" ,"POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2014 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 25)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_5_6 trop_nights.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_5_6 trop_nights.png"),plot=h,
       width = 2666/250,
       height= 1875/250,
       unit="in")

```
### 6 tropical night classes

#### 3 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  #filter(temperature  %in% c("[12;14[","[10;12["))%>% 
  #filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  group_by(LULC,POP,AGE ) %>% 
  summarise(value=sum(value)) %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1 149 599
#65+ 2018: 1 812 696
# pop totale Idf 1990: 10 644 665
# pop totale Idf 2018: 12 213 447



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/1812696*1149599,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*1812696/1149599,value))

df_tmp <- rbind(df2,df3)


perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed\nto more than 10 tropical nights",  subtitle = "Thousands of people, age 65+")
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population\nnumber",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=5)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_3_6 trop_nights.png"),plot=g,
       width = 2666/280,
       height= 1875/280,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_3_6 trop_nights.png"),plot=h,
       width = 2666/280,
       height= 1875/280,
       unit="in")
```



#### 4 categories

```{r}

df <- exposure_tropnight_classe_65_plus_new %>% 
  filter(temperature  %in% c("[12;14[","[10;12[","[8;10[","[6;8["))%>% 
  #filter(temperature  %in% c("[12;14[")) %>% 
  dplyr::select(-temperature) %>% 
  group_by(LULC,POP,AGE ) %>% 
  summarise(value=sum(value)) %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

ratio_65_1990 = 1149599/10644665 
ratio_65_2018 = 1812696/12213447 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","REP_age" ,"POP" ,"LULC","value")

perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n6 tropical nights",  subtitle = "Thousands of people, age 65+C",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n6 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_4_6 trop_nights.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_4_6 trop_nights.png"),plot=h,
       width = 2666/250,
       height= 1875/250,
       unit="in")

```

#### 5 classes

```{r}
final_data <- read_parquet("./data/final_data_consecutive.parquet")

window_size=15

df <- final_data %>%
  arrange(year) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >=6,
         seuil_90 = nb_nuit_trop_C >= 6) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    #value = slide_index_dbl(value,year,~ as.numeric(quantile(.x, probs = 0.,na.rm = TRUE)),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2014,2022))


ratio_65_1990 = 1149599/10644665 
ratio_65_2018 = 1812696/12213447 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","REP_age" ,"POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2014 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n6 consecutive tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 35)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n6 tropical nights")+
  geom_hline(yintercept =0)


ggsave(paste0("./outputs/shapley_5_6 trop_nights.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")

ggsave(paste0("./outputs/shapley_distrib_5_6 trop_nights.png"),plot=h,
       width = 2666/250,
       height= 1875/250,
       unit="in")

```
### tn

#### 3 classes

```{r}
df <- exposure_tn_p90_classes_65_plus_new %>% 
  #filter(temperature == "[20;21[") %>% 
  filter(temperature  %in% c("[19;20[","[20;21["))%>% 
  dplyr::select(-temperature) %>% 
  group_by(LULC,POP,AGE ) %>% 
  summarise(value=sum(value)) %>%
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)


#65+ 1990: 1 149 599
#65+ 2018: 1 812 696
# pop totale Idf 1990: 10 644 665
# pop totale Idf 2018: 12 213 447



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/1812696*1149599,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*1812696/1149599,value))

df_tmp <- rbind(df2,df3)


perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18)
g

perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable,\nfor all permutations",
          subtitle = "Thousands of people, age 65+, Tn > 15°C")+
  geom_hline(yintercept =0)
```

#### 4 classes

```{r}
df <- exposure_tn_p90_classes_65_plus_new %>% 
  filter(temperature == "[16;17[") %>% 
  filter(AGE == POP) %>% 
  dplyr::select(-AGE)

#65+ 1990: 1149599
#65+ 2018: 1812696
# pop totale Idf 1990: 10644665
# pop totale Idf 2018: 12213447

ratio_65_1990 = 1149599/10644665  
ratio_65_2018 = 1812696/12213447  

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value/12213447*10644665,value))

df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value*12213447/10644665,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","REP_age" ,"POP" ,"LULC","value")

perm_df <- compute_permut(df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  )

g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18)
g

perm_df %>% 
  ggplot(aes(x=variable,y=contribution))+
  geom_jitter()
```


# que petite couronne et paris
## 3 classes + year
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2014,2022))

pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_65_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2014 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)

h
# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```

## 3 classes 
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  summarise(
    value = mean(value)   )

pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_65_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_65_1990,value))


df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","POP" ,"LULC","value") 

perm_df <- compute_permut(df_tmp,vars = c( "REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("REP","POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 25)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```
## 5 classes
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2014,2022))


pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(95,93,92,75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )

ratio_65_1990 = pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_totale_1990 
ratio_65_2018 = pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_totale_2018 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_totale_1990/pop_totale_tmp$pop_totale_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_totale_2018/pop_totale_tmp$pop_totale_1990,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","REP_age" ,"POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2014 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)

h
# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```

# que paris
## 3 classes + year
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2014,2022))

pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )



df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_65_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2014 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)

h
# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```

## 3 classes 
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  summarise(
    value = mean(value)   )

pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_65_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_65_1990,value))


df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("REP","POP" ,"LULC","value") 

perm_df <- compute_permut(df_tmp,vars = c( "REP",  "POP","LULC"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("REP","POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 25)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)


# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```
## 5 classes
```{r}
window_size=15

df <- final_data %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  mutate(seuil_18 = nb_nuit_trop_D >10,
         seuil_90 = nb_nuit_trop_C > 10) %>% 
  group_by(year,INSEE_COM) %>% 
  summarise(
    LULC90_POP90 = sum( `65+_90` * seuil_90 ),
    LULC90_POP18 = sum( `65+_18` * seuil_90 ),
    LULC18_POP90 = sum( `65+_90` * seuil_18 ),
    LULC18_POP18 = sum( `65+_18` * seuil_18 )
  ) %>% 
  pivot_longer(cols=-c(year,INSEE_COM)) %>% 
  separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
  separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
  separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
  group_by(year,LULC,POP) %>% 
  summarise(value=sum(value))%>% 
  group_by(LULC,POP ) %>% 
  mutate(
    value = slide_index_dbl(value,year,~ mean(.x, na.rm = TRUE),.before = window_size-1,.complete = FALSE),   # 10-year window ending at current year
    window = slide_index(
      year,
      year,
      ~ paste0(min(.x), "-", max(.x)),
      .before = window_size-1,
      .complete = FALSE
    ),
        # number of years in window
    n_years = slide_index_int(
      value,
      year,
      ~ length(.x),
      .before = window_size-1,
      .complete = FALSE
    )
  )%>% 
  filter(n_years == window_size) %>% 
  filter(year %in% c(2000+window_size-1,2022))


pop_totale_tmp <- final_data %>% 
  filter(year == 2020) %>% 
  filter(INSEE_DEP %in% c(75)) %>% 
  ungroup() %>% 
  summarise(
    pop_totale_1990 = sum(popTOT_90),
    pop_totale_2018 = sum(popTOT_18),
    pop_65_1990 = sum(`65+_90`),
    pop_65_2018 = sum(`65+_18`),
  )

ratio_65_1990 = pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_totale_1990 
ratio_65_2018 = pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_totale_2018 

df2<- df %>% 
  mutate(REP = 90,
         value=if_else(POP==18,value * pop_totale_tmp$pop_totale_1990/pop_totale_tmp$pop_totale_2018,value))
  
df3 <- df %>% 
  mutate(REP = 18, 
         value=if_else(POP==90,value * pop_totale_tmp$pop_totale_2018/pop_totale_tmp$pop_totale_1990,value))

df_tmp <- rbind(df2,df3)

df2<- df_tmp %>% 
  mutate(REP_age = 90,
         value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))

df3 <- df_tmp %>% 
  mutate(REP_age = 18, 
         value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))

df_tmp <- rbind(df2,df3) %>% 
  dplyr::select("year","REP","REP_age" ,"POP" ,"LULC","value") %>% 
  mutate(year = case_when(
    year == 2000+window_size-1 ~ 90,
    year == 2022 ~ 18
  ))

perm_df <- compute_permut(df_tmp,vars = c("year" , "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",

shapley_df <- perm_df %>%
  group_by(variable) %>%
  summarise(
    shapley = mean(contribution),
    .groups = "drop"
  ) %>% 
  mutate(ordre=factor(variable,levels = c("year","REP","REP_age", "POP","LULC")))


g <- draw_waterfall(shapley_df,df_tmp,vars = c("year","REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = "Number of people exposed to more than\n10 tropical nights",  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 20)
g

h <- perm_df %>% 
    mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "UHI variation",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
  ggplot(aes(x=variable,y=contribution/1000))+
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
    bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle("Influence of each variable, for all permutations",
          subtitle = "Thousands of people, age 65+, exposed to more than\n10 tropical nights")+
  geom_hline(yintercept =0)

h
# ggsave(paste0("./outputs/shapley_5_10 trop_nights.png"),plot=g,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")
# 
# ggsave(paste0("./outputs/shapley_distrib_5_10 trop_nights.png"),plot=h,
#        width = 2666/250,
#        height= 1875/250,
#        unit="in")

```


# analyse par canicule 

## tropical nights
### calcul et graphes détaillés

```{r, warnings=False }

memoire_df <- data_frame()

for (year_ici in c(2017,2018,2019,2020,2022))
{
  
  for (seuil in c(10)) #seq(3,12))
  {
    
    
    tmp <- final_data %>% 
      filter(year == year_ici)
    
    df <- final_data %>% 
      filter(year == year_ici) %>% 
      mutate(seuil_18 = nb_nuit_trop_D >seuil,
             seuil_90 = nb_nuit_trop_C > seuil) %>% 
      group_by(year,INSEE_COM) %>% 
      summarise(
        LULC90_POP90 = sum( `65+_90` * seuil_90 ),
        LULC90_POP18 = sum( `65+_18` * seuil_90 ),
        LULC18_POP90 = sum( `65+_90` * seuil_18 ),
        LULC18_POP18 = sum( `65+_18` * seuil_18 ),
        .groups = "drop_last"
      ) %>% 
      pivot_longer(cols=-c(year,INSEE_COM)) %>% 
      separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
      separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
      separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
      group_by(,LULC,POP) %>% 
      summarise(value=sum(value),.groups = "drop_last")
    
    pop_totale_tmp <- final_data %>% 
      filter(year == 2020) %>% #peu importe, c'est juste pour ne garder qu'une année
      ungroup() %>% 
      summarise(
        pop_totale_1990 = sum(popTOT_90),
        pop_totale_2018 = sum(popTOT_18),
        pop_65_1990 = sum(`65+_90`),
        pop_65_2018 = sum(`65+_18`),
      )
    
    ratio_65_1990 = pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_totale_1990 
    ratio_65_2018 = pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_totale_2018 
    
    df2<- df %>% 
      mutate(REP = 90,
             value=if_else(POP==18,value * pop_totale_tmp$pop_totale_1990/pop_totale_tmp$pop_totale_2018,value))
    
    df3 <- df %>% 
      mutate(REP = 18, 
             value=if_else(POP==90,value * pop_totale_tmp$pop_totale_2018/pop_totale_tmp$pop_totale_1990,value))
    
    df_tmp <- rbind(df2,df3)
    
    df2<- df_tmp %>% 
      mutate(REP_age = 90,
             value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))
    
    df3 <- df_tmp %>% 
      mutate(REP_age = 18, 
             value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))
    
    df_tmp <- rbind(df2,df3) %>% 
      dplyr::select("REP","REP_age" ,"POP" ,"LULC","value") 
    
    perm_df <- compute_permut(df_tmp,vars = c(  "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",
    
    shapley_df <- perm_df %>%
      group_by(variable) %>%
      summarise(
        shapley = mean(contribution),
        .groups = "drop"
      ) %>% 
      mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))
    
    min_max <- perm_df %>% 
      group_by(variable) %>% 
      summarise(mini = min(contribution),
                maxi = max(contribution),
                quant75 = quantile(contribution,probs = 0.75),
                quant25 = quantile(contribution,probs = 0.25))
    
    #variable qui stocke les resultats du shapley
    memoire_df <- shapley_df %>% 
      dplyr::select(-variable) %>% 
      mutate(year = year_ici,
             seuil = seuil) %>% 
      left_join(min_max,by = c("ordre" = "variable")) %>% 
      rbind(memoire_df) 
      
    
    if (draw_ici) 
    {
      g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = paste0(year_ici," summer, number of people exposed to\nmore than ",seuil," tropical nights"),  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 80)
      g
      
      h <- perm_df %>% 
        mutate(variable = as.factor(case_when(
          # variable == "LULC" ~ "impact of\nland-use change\non urban climate",
          # variable == "year" ~ "climate change",
          # variable == "AGE" ~ "change in the ratio\nof people aged 65+\nin the population",
          # variable == "POP" ~ "change in the\nlocation of people\naged 65+ within\nthe region",
          # variable == "REP" ~ "global population\nincrease in the\nregion",
          # variable == "REP_age" ~ "change in the ratio\nof people aged 65+\nin the population",
          variable == "LULC" ~ "Land-use change\n(urban\nclimate)",
          variable == "year" ~ "Climate change",
          variable == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
          variable == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
          variable == "REP" ~ "Total population\nincrease",
          variable == "REP_age" ~ "Population\nage structure",
          TRUE ~ variable))) %>% 
        ggplot(aes(x=variable,y=contribution/1000))+
        geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
        #geom_boxplot(alpha=0.,outlier.shape = NA)+
        bbc_style()+
        theme(legend.position = "none",
              axis.text.x = element_text(angle=0,size=16),) +
        ggtitle("Influence of each variable, for all permutations",
                subtitle = paste0(year_ici," summer, thousands of people, age 65+,\nexposed to more than ",seuil," tropical nights"))+
        geom_hline(yintercept =0)
      
      h
      
      ggsave(paste0("./outputs/par_canicule/canicule_",year_ici,"_",seuil,".png"),plot=g,
             width = 2666/250,
             height= 1875/250,
             unit="in")
      
      ggsave(paste0("./outputs/par_canicule/distrib_canicule_",year_ici,"_",seuil,".png"),plot=h,
             width = 2666/250,
             height= 1875/250,
             unit="in")
    }
  }
}

#write_parquet(memoire_df,"./data/memoire_df.parquet")
```

### graphe résumé

```{r}

memoire_df <- read_parquet("./data/memoire_df.parquet")

g <- memoire_df %>% 
  mutate(ordre = case_when(
    ordre == "LULC" ~ "Land-use change\n(urban climate)",
    ordre == "year" ~ "Climate change",
    ordre == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
    ordre == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
    ordre == "REP" ~ "Total population\nincrease",
    ordre == "REP_age" ~ "Population\nage structure",
    TRUE ~ ordre)) %>% 
  ggplot(aes(x=seuil,y=shapley,group=ordre,color=ordre,fill = ordre))+
  geom_line()+
  geom_ribbon(aes(ymin = mini, ymax = maxi),
              alpha = 0.3,
              color = NA) +
  facet_wrap(~year)+
  geom_hline(yintercept = 0)+
  bbc_style()+
  labs(x="Number of tropical nights",y="Change in number of people 65+\nexposed to persistent\ntropical-night exposure")+
  ggtitle("Evolution of the contribution of each variable",
          subtitle = "When changing the number of tropical nights")+
  theme(axis.ticks.x = element_line(colour = "#333333"),
        axis.ticks.length =  unit(0.26, "cm"),
        axis.title = ggplot2::element_text( size = 18, color = "#222222"))+
  scale_x_continuous(breaks = seq(3,12,))

g
ggsave(paste0("./outputs/par_canicule/summary.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```

## consecutive tropical nights

```{r, warnings=False }


memoire_df_consecutive <- data_frame()

for (seuil in seq(3,6))
{
  for (year_ici in c(2003,2017,2018,2019,2020,2022))
  {
    
    df <- final_data_consecutive %>% 
      filter(year == year_ici) %>% 
      mutate(seuil_18 = nb_nuit_trop_D >seuil,
             seuil_90 = nb_nuit_trop_C > seuil) %>% 
      group_by(year,INSEE_COM) %>% 
      summarise(
        LULC90_POP90 = sum( `65+_90` * seuil_90 ),
        LULC90_POP18 = sum( `65+_18` * seuil_90 ),
        LULC18_POP90 = sum( `65+_90` * seuil_18 ),
        LULC18_POP18 = sum( `65+_18` * seuil_18 ),
        .groups = "drop_last"
      ) %>% 
      pivot_longer(cols=-c(year,INSEE_COM)) %>% 
      separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
      separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
      separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
      group_by(,LULC,POP) %>% 
      summarise(value=sum(value),.groups = "drop_last")
    
    
    pop_totale_tmp <- final_data %>% 
      filter(year == 2020) %>% 
      ungroup() %>% 
      summarise(
        pop_totale_1990 = sum(popTOT_90),
        pop_totale_2018 = sum(popTOT_18),
        pop_65_1990 = sum(`65+_90`),
        pop_65_2018 = sum(`65+_18`),
      )
    
    ratio_65_1990 = pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_totale_1990 
    ratio_65_2018 = pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_totale_2018 
    
    df2<- df %>% 
      mutate(REP = 90,
             value=if_else(POP==18,value * pop_totale_tmp$pop_totale_1990/pop_totale_tmp$pop_totale_2018,value))
    
    df3 <- df %>% 
      mutate(REP = 18, 
             value=if_else(POP==90,value * pop_totale_tmp$pop_totale_2018/pop_totale_tmp$pop_totale_1990,value))
    
    df_tmp <- rbind(df2,df3)
    
    df2<- df_tmp %>% 
      mutate(REP_age = 90,
             value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))
    
    df3 <- df_tmp %>% 
      mutate(REP_age = 18, 
             value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))
    
    df_tmp <- rbind(df2,df3) %>% 
      dplyr::select("REP","REP_age" ,"POP" ,"LULC","value") 
    
    perm_df <- compute_permut(df_tmp,vars = c(  "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",
    
    shapley_df <- perm_df %>%
      group_by(variable) %>%
      summarise(
        shapley = mean(contribution),
        .groups = "drop"
      ) %>% 
      mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))
    
    min_max <- perm_df %>% 
      group_by(variable) %>% 
      summarise(mini = min(contribution),
                maxi = max(contribution),
                quant75 = quantile(contribution,probs = 0.75),
                quant25 = quantile(contribution,probs = 0.25))
    
    #variable qui stocke les resultats du shapley
    memoire_df <- shapley_df %>% 
      dplyr::select(-variable) %>% 
      mutate(year = year_ici,
             seuil = seuil) %>% 
      left_join(min_max,by = c("ordre" = "variable")) %>% 
      rbind(memoire_df) 
    
    if (draw_ici) 
    {
      g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = paste0(year_ici," summer, number of people exposed to\nmore than ",seuil," consecutive tropical nights"),  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 80)
      g
      
      h <- perm_df %>% 
        mutate(variable = as.factor(case_when(
          variable == "LULC" ~ "impact of\nland-use change\non urban climate",
          variable == "year" ~ "climate change",
          variable == "AGE" ~ "change in\npopulation age",
          variable == "POP" ~ "change in\npopulation location",
          variable == "REP" ~ "change in\ntotal population",
          variable == "REP_age" ~ "change in\npopulation age",
          TRUE ~ variable))) %>% 
        ggplot(aes(x=variable,y=contribution/1000))+
        geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
        #geom_boxplot(alpha=0.,outlier.shape = NA)+
        bbc_style()+
        theme(legend.position = "none",
              axis.text.x = element_text(angle=0,size=16),) +
        ggtitle("Influence of each variable, for all permutations",
                subtitle = paste0(year_ici," summer, thousands of people, age 65+,\nexposed to more than ",seuil," consecutive tropical nights"))+
        geom_hline(yintercept =0)
      
      h
      
      ggsave(paste0("./outputs/par_canicule_consecutive/canicule_",year_ici,"_",seuil,".png"),plot=g,
             width = 2666/250,
             height= 1875/250,
             unit="in")
      
      ggsave(paste0("./outputs/par_canicule_consecutive/distrib_canicule_",year_ici,"_",seuil,".png"),plot=h,
             width = 2666/250,
             height= 1875/250,
             unit="in")
    }
  }
}

write_parquet(memoire_df_consecutive,"./data/memoire_df_consecutive.parquet")
```
### test evolution des shapley

```{r}
g <- memoire_df_consecutive %>% 
  mutate(ordre = case_when(
    ordre == "LULC" ~ "impact of\nland-use change\non urban climate",
    ordre == "year" ~ "climate change",
    ordre == "AGE" ~ "change in\npopulation age",
    ordre == "POP" ~ "change in\npopulation location",
    ordre == "REP" ~ "change in\ntotal population",
    ordre == "REP_age" ~ "change in\npopulation age",
    TRUE ~ ordre)) %>% 
  ggplot(aes(x=seuil,y=shapley,group=ordre,color=ordre))+
  geom_ribbon(aes(ymin = mini, ymax = maxi),
              alpha = 0.3,
              color = NA) +
  facet_wrap(~year)+
  geom_hline(yintercept = 0)+
  bbc_style()+
  labs(x="number of tropical nights",y="contribution of each variable")+
  ggtitle("Evolution of the contribution of each variable",
          subtitle = "When changing the number of tropical nights")+
  theme(axis.ticks.x = element_line(colour = "#333333"),
        axis.ticks.length =  unit(0.26, "cm"))+
  scale_x_continuous(breaks = seq(3,12,))


ggsave(paste0("./outputs/par_canicule_consecutive/summary.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```

## 25 degrees

```{r}
final_data <- read_parquet("./data/final_data.parquet")

for (seuil in seq(3,3))
{
  for (year_ici in c(2017,2018,2019,2020,2022))
  {
    
    tmp <- final_data %>% 
      filter(year == year_ici)
    
    df <- final_data %>% 
      filter(year == year_ici) %>% 
      mutate(seuil_18 = nb_nuit_trop_D_25 >seuil,
             seuil_90 = nb_nuit_trop_C_25 > seuil) %>% 
      group_by(year,INSEE_COM) %>% 
      summarise(
        LULC90_POP90 = sum( `65+_90` * seuil_90 ),
        LULC90_POP18 = sum( `65+_18` * seuil_90 ),
        LULC18_POP90 = sum( `65+_90` * seuil_18 ),
        LULC18_POP18 = sum( `65+_18` * seuil_18 )
      ) %>% 
      pivot_longer(cols=-c(year,INSEE_COM)) %>% 
      separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
      separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
      separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
      group_by(,LULC,POP) %>% 
      summarise(value=sum(value))
    
    
    ratio_65_1990 = 1149599/10644665 
    ratio_65_2018 = 1812696/12213447 
    
    df2<- df %>% 
      mutate(REP = 90,
             value=if_else(POP==18,value/12213447*10644665,value))
    
    df3 <- df %>% 
      mutate(REP = 18, 
             value=if_else(POP==90,value*12213447/10644665,value))
    
    df_tmp <- rbind(df2,df3)
    
    df2<- df_tmp %>% 
      mutate(REP_age = 90,
             value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))
    
    df3 <- df_tmp %>% 
      mutate(REP_age = 18, 
             value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))
    
    df_tmp <- rbind(df2,df3) %>% 
      dplyr::select("REP","REP_age" ,"POP" ,"LULC","value") 
    
    perm_df <- compute_permut(df_tmp,vars = c(  "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",
    
    shapley_df <- perm_df %>%
      group_by(variable) %>%
      summarise(
        shapley = mean(contribution),
        .groups = "drop"
      ) %>% 
      mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))
    
    
    g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = paste0(year_ici," summer, number of people exposed to\nmore than ",seuil," nights > 25 °C"),  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 80)
    g
    
    h <- perm_df %>% 
      mutate(variable = as.factor(case_when(
        variable == "LULC" ~ "impact of\nland-use change\non urban climate",
        variable == "year" ~ "climate change",
        variable == "AGE" ~ "change in\npopulation age",
        variable == "POP" ~ "change in\npopulation location",
        variable == "REP" ~ "change in\ntotal population",
        variable == "REP_age" ~ "change in\npopulation age",
        TRUE ~ variable))) %>% 
      ggplot(aes(x=variable,y=contribution/1000))+
      geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
      #geom_boxplot(alpha=0.,outlier.shape = NA)+
      bbc_style()+
      theme(legend.position = "none",
            axis.text.x = element_text(angle=0,size=16),) +
      ggtitle("Influence of each variable, for all permutations",
              subtitle = paste0(year_ici," summer, thousands of people, age 65+,\nexposed to more than ",seuil,"  nights > 25° C"))+
      geom_hline(yintercept =0)
    
    h
    
    ggsave(paste0("./outputs/par_canicule_25/canicule_",year_ici,"_",seuil,".png"),plot=g,
           width = 2666/250,
           height= 1875/250,
           unit="in")
    
    ggsave(paste0("./outputs/par_canicule_25/distrib_canicule_",year_ici,"_",seuil,".png"),plot=h,
           width = 2666/250,
           height= 1875/250,
           unit="in")
    
  }
}
```

