---
title: "Papier GPE2"
output: html_notebook
---
# data loading
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo = FALSE,warning = FALSE, message=FALSE)

library(tidyverse)
library(readxl)
library(readr)
library(shadowtext)
library(ggrepel)
library('bbplot')
library(waterfalls)
library(directlabels)
library(forcats)

SAVE_ici<-TRUE
```

```{r import data}
#result<-read.csv('data/result.csv',sep = "\t")

result<-read.csv('data/match_40/results_match_40_multiplicatif.csv',sep = ",") %>% 
  mutate('match'="match_40")

for (namei in c("match_20","match_60","no_match_40")){
tmp<-read.csv(paste0('data/',namei,'/results_',namei,'_multiplicatif.csv'),sep = ",") %>% 
  mutate('match'=namei)
result<-rbind(result, tmp)
}

result<-result %>% 
  pivot_longer(2:5,names_to="group")%>% 
  mutate(group=case_when(
    group=='group2' ~ "Group 1\n(high income)",
    group=='group3' ~ "Group 2\n(middle income)",
    group=='group4' ~ "Group 3\n(low income)",
    group=='group5' ~ "Group 4\n(low income)"
  ))

result2<-result%>% 
  mutate(year=str_wrap(year,width=6))

#weighted_accessibility<-read.csv('data/weighted_accessibility.csv',sep = "\t")
weighted_accessibility<-read.csv('data/match_40/weighted_accessibility_match_40.csv',sep = ",") %>% 
  rename('year'='X') %>% 
  pivot_longer(cols=-1,names_to = 'group') %>% 
  mutate(group=case_when(
    group=='group2' ~ "Group 1\n(high income)",
    group=='group3' ~ "Group 2\n(middle income)",
    group=='group4' ~ "Group 3\n(low income)",
    group=='group5' ~ "Group 4\n(low income)"
  ))

# add 'Real accessibility gains (%)'
result <- result %>% 
  select(-X) %>% 
  pivot_wider(names_from = name,values_from = value) %>% 
  mutate(`Real accessibility gains (%)`= 100*(1+`Job growth (%)`/100)*(1+`Speed (%)`/100)*(1+`Proximity (%)`/100)-100) %>% 
  rename('Proximity - households (%)'='Proximity - hh (%)') %>% 
  pivot_longer(-c(year,match,group)) 

```

# curves
## weighted accessibility
```{r weighted accessibility}


p<-ggplot(weighted_accessibility,aes(x=year,y=value,group=group))+
  geom_line(aes(color=group),show.legend = TRUE,size=1)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        #legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    #legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  #geom_dl(aes(label = group,color=group), method = list("last.qp",cex=1.2,hjust = +2))+
  #xlim(1968,2017)+
  labs(title = "Weighted accessibility to jobs",subtitle = "Historical evolution in Île de France region")
#direct.label(p,method=list("angled.boxes",cex=1))

if (SAVE_ici) {
ggsave(paste0("./outputs/line_evol_absolu.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
p
```

```{r weighted accessibility index}

tmp<-weighted_accessibility %>% 
  filter(year==1968)%>% 
  select(-year) %>% 
  rename(valeur_initiale=value)

p<-weighted_accessibility %>% 
  left_join(.,tmp) %>% 
  mutate(value=value/valeur_initiale) %>% 
  select(-valeur_initiale) %>% 
ggplot(aes(x=year,y=value,group=group))+
  geom_line(aes(color=group),show.legend = TRUE,size=1)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(title = "Weighted accessibility to jobs (index)",subtitle = "Evolution relative to 1968")
#direct.label(p,method=list("angled.boxes",cex=1))

if (SAVE_ici) {
ggsave(paste0("./outputs/line_evol_index.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
p
```
## useless lines

```{r lines}
for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){

p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
ggplot(aes(x=year,y=value,group=group))+
  geom_line(aes(color=group),show.legend = TRUE,size=1)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "right", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(title = nami)

if (SAVE_ici) {
ggsave(paste0("./outputs/test.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)
}
```

# decomposition par driver d'évolution (bars)

## toutes les decompositions possibles
```{r bars}
for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){

    nami2=case_when(
    nami=='Speed (%)' ~ 'Public Transport improvements',
    nami=='Proximity (%)' ~ 'Changes in spatial proximity to jobs',
    nami=='Job growth (%)' ~ 'Changes in total number of matching jobs',
    nami=="Proximity - households (%)" ~ 'Changes in spatial proximity to jobs: impact\nof the locations of households',
    nami=="Proximity - jobs (%)" ~ 'Changes in spatial proximity to jobs: impact\nof the locations of jobs',
    TRUE ~ nami
    )
  nami2
  nami
p<-result %>% 
  filter(match=='match_40',
         name==nami
         )  %>% 
ggplot(aes(x=year,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,width=0.6)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm")
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(title = nami2,subtitle = 'Impact on accessibility (variation in %)')

if (SAVE_ici) {
ggsave(paste0("./outputs/bars_",substr(nami,1,nchar(nami)-3),".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)
}
```
## graphes un peu plus travaillés
### effet a priori du TC
```{r bars TC}
#for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
nami='Speed (%)'
p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
ggplot(aes(x=year,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,size=1)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(subtitle = "Accessibility gains per labor group (%)",title="Impact of public transport improvements")

if (SAVE_ici) {
ggsave(paste0("./outputs/bars_TC.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)
#}
```
### accessibilite totale
```{r bars all accessibility}
#for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
nami='Real accessibility gains (%)'
p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
ggplot(aes(x=year,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,width=0.6)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(subtitle = "Difference in accessibility in each time period (%)",title="Accessibility variations")

if (SAVE_ici) {
ggsave(paste0("./outputs/bars_Total.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)
#}
```
# waterfall graphs

## (useless) waterfall per year
```{r waterfall all}
for (groupi in unique(result$group)){

nami<-"Real accessibility gains (%)"

result3 <- result %>% 
  filter(match=='match_40',
         name==nami,
         group==groupi
         )

p<-waterfall(labels = result3$year,values = result3$value,
             rect_text_labels=round(result3$value),
             rect_text_size=2,
             put_rect_text_outside_when_value_below=10)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  #geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ylim(-70,120)+
  labs(title = nami,subtitle=groupi)
  

if (SAVE_ici) {
ggsave(paste0("./outputs/waterfall_",groupi,".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
p
}
```

## (useless) waterfall per year for each decomposition

```{r waterfall job}
for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
for (groupi in unique(result$group)){

result3 <- result %>% 
  filter(match=='match_40',
         name==nami,
         group==groupi
         )

p<-waterfall(labels = result3$year,values = result3$value,
             rect_text_labels=round(result3$value),
             rect_text_size=2,
             put_rect_text_outside_when_value_below=10)+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  # geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  ylim(-70,120)+
  labs(title = nami,subtitle=groupi)
  

if (SAVE_ici) {
ggsave(paste0("./outputs/waterfall_",str_sub(nami,1,nchar(nami)-4),"_",groupi,".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
}
}

p
```

## (useless) non-log waterfall by group for entire period

```{r waterfall job global}
#for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
for (groupi in unique(result$group)){

nami<-c('Real accessibility gains (%)',"Proximity - households (%)","Proximity - jobs (%)")
#groupi<-"group3"

result4 <- result %>% 
  filter(match=='match_40',
         #transport=='TC',
         !(name %in% nami),
         group==groupi
         ) %>% 
  mutate(name2=name,
         name=case_when(
    name=='Speed (%)' ~ 'Public Transport\nimprovements',
    name=='Proximity (%)' ~ 'Changes in\nspatial proximity\nto jobs',
    name=='Job growth (%)' ~ 'Changes in\ntotal number\nof matching jobs',)) %>% 
  #mutate(name=fct_reorder(name,name2)) %>% 
  #mutate(name=factor(name,levels=name2)) %>% 
  #select(-name2) %>% 
  #mutate(name=as.character( name )) %>% 
  group_by(name,name2,group) %>% 
  summarise(value=sum(value)) %>% 
    arrange(name2) 

p<-waterfall(labels = result4$name,values = result4$value,
             rect_text_labels=sprintf("%+d %%",round(result4$value)),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=15,
             calc_total=TRUE,
             #total_axis_text=nami,
             total_rect_text=ifelse(abs(round(sum(result4$value)))<10,'',sprintf("%+d %%",round(sum(result4$value)))))+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=18),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  # geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  #ylim(-100,120)+
  labs(subtitle = 'Accessibility variations 1968-2010 (%)',title=gsub("[\r\n]", "  ", groupi))
  

if (SAVE_ici) {
ggsave(paste0("./outputs/overall_waterfall_",str_sub(nami[1],1,nchar(nami[1])-4),"_",groupi,".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
}
#}

p
```

## log waterfall by group for entire period

```{r waterfall job global log}
#for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
for (groupi in unique(result$group)){

nami<-c('Real accessibility gains (%)',"Proximity - households (%)","Proximity - jobs (%)")#
#groupi<-"group3"

result4 <- result %>% 
  filter(match=='match_40',
         #transport=='TC',
         !(name %in% nami),
         group==groupi
         ) %>% 
  mutate(name2=name,
         name=case_when(
    name=='Speed (%)' ~ 'Public Transport\nimprovements',
    name=='Proximity (%)' ~ 'Changes in\nspatial proximity\nto jobs',
    name=='Job growth (%)' ~ 'Changes in\ntotal number\nof matching jobs',)) %>% 
  #mutate(name=fct_reorder(name,name2)) %>% 
  #mutate(name=factor(name,levels=name2)) %>% 
  #select(-name2) %>% 
  #mutate(name=as.character( name )) %>% 
  group_by(name,name2,group) %>% 
  summarise(value=100*(prod(1+value/100)-1)) %>% 
    arrange(name2)%>% 
    mutate(value2=100*log(1+value/100)) 

kk<-function(y) 100*log(1+y/100)
kj<-function(y) 100*(exp(y/100)-1)

# tn <- trans_new(name="log_custom",
#                 transform=function(y) log(1+y/100),
#                 inverse=function(y) 100*(exp(y)-1),
#                 domain=c(-100, Inf))

p<-waterfall(labels = result4$name,values = result4$value2,
             rect_text_labels=sprintf("%+d %%",round(result4$value)),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=15,
             calc_total=TRUE,
             #total_axis_text=nami,
             total_rect_text=ifelse(abs(round(sum(result4$value2)))<10,'',sprintf("%+d %%",round(100*(prod(1+result4$value/100)-1)))))+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=18),
        #axis.text.y = element_blank(),
        #panel.grid.major.y = element_blank(),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  # geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  # scale_y_continuous(trans=tn,breaks =seq(-100,100,10) )+
  scale_y_continuous(breaks =kk(c(seq(-75,0,25),seq(50,200,50))),labels = kj,limits=c(-85,105))+
  #ylim(-100,105)+
  labs(subtitle = 'Accessibility variations 1968-2010 (%)',title=gsub("[\r\n]", "  ", groupi))
  

if (SAVE_ici) {
ggsave(paste0("./outputs/log_overall_waterfall_",str_sub(nami[1],1,nchar(nami[1])-4),"_",groupi,".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
}
#}

p

```
## log waterfall avec decomposition proximity
```{r waterfall job global log}
#for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){
for (groupi in unique(result$group)){

nami<-c('Real accessibility gains (%)',"Proximity (%)")#"Proximity - households (%)","Proximity - jobs (%)",
#groupi<-"group3"

result4 <- result %>% 
  filter(match=='match_40',
         #transport=='TC',
         !(name %in% nami),
         group==groupi
         ) %>% 
  mutate(name2=name,
         name=case_when(
    name=='Speed (%)' ~ 'Public Transport\nimprovements',
    name=="Proximity - jobs (%)" ~ 'Locations\nof jobs',
    name=="Proximity - households (%)" ~ 'Locations of\nhouseholds',
    name=='Job growth (%)' ~ 'Changes in\ntotal number\nof matching jobs',)) %>% 
  #mutate(name=fct_reorder(name,name2)) %>% 
  #mutate(name=factor(name,levels=name2)) %>% 
  #select(-name2) %>% 
  #mutate(name=as.character( name )) %>% 
  group_by(name,name2,group) %>% 
  summarise(value=100*(prod(1+value/100)-1)) %>% 
    arrange(name2)%>% 
    mutate(value2=100*log(1+value/100)) 

kk<-function(y) 100*log(1+y/100)
kj<-function(y) 100*(exp(y/100)-1)

# tn <- trans_new(name="log_custom",
#                 transform=function(y) log(1+y/100),
#                 inverse=function(y) 100*(exp(y)-1),
#                 domain=c(-100, Inf))

p<-waterfall(labels = result4$name,values = result4$value2,
             rect_text_labels=sprintf("%+d %%",round(result4$value)),
             rect_text_size=3,
             put_rect_text_outside_when_value_below=15,
             calc_total=TRUE,
             #total_axis_text=nami,
             total_rect_text=ifelse(abs(round(sum(result4$value2)))<10,'',sprintf("%+d %%",round(100*(prod(1+result4$value/100)-1)))))+
  bbc_style()+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=18),
        #axis.text.y = element_blank(),
        #panel.grid.major.y = element_blank(),
        ) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  # geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  # scale_y_continuous(trans=tn,breaks =seq(-100,100,10) )+
  scale_y_continuous(breaks =kk(c(seq(-75,0,25),seq(50,200,50))),labels = kj,limits=c(-85,105))+
  #ylim(-100,105)+
  labs(subtitle = 'Accessibility variations 1968-2010 (%)',title=gsub("[\r\n]", "  ", groupi))
  

if (SAVE_ici) {
ggsave(paste0("./outputs/log_overall_detailed_waterfall_",str_sub(nami[1],1,nchar(nami[1])-4),"_",groupi,".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}
p
}
#}


```

# global evolution
## ex ante
```{r}
nami='Speed (%)'
p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
  group_by(group) %>% 
  summarise(value=(prod(1+value/100))*100-100) %>% 
  ggplot(aes(x=group,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,width=0.6)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(subtitle = "Accessibility gains per labor group, 1968-2010 (%)",title="Ex ante impact of public transport improvements")

if (SAVE_ici) {
ggsave(paste0("./outputs/ex_ante.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)

```
## ex post
```{r}
nami='Real accessibility gains (%)'
p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
  group_by(group) %>% 
  summarise(value=(prod(1+value/100))*100-100) %>% 
  ggplot(aes(x=group,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,width=0.6)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(subtitle = "Accessibility gains per labor group, 1968-2010 (%)",title="Actual (total) accessibility variations")

if (SAVE_ici) {
ggsave(paste0("./outputs/ex_post.png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)

```

## decomnposition par driver

```{r}
for (nami in c('Job growth (%)','Real accessibility gains (%)','Speed (%)','Proximity (%)',"Proximity - households (%)","Proximity - jobs (%)")){

    nami2=case_when(
    nami=='Speed (%)' ~ 'Public Transport improvements',
    nami=='Proximity (%)' ~ 'Changes in spatial proximity to jobs',
    nami=='Job growth (%)' ~ 'Changes in total number of matching jobs',
    nami=="Proximity - households (%)" ~ 'Changes in spatial proximity to jobs: impact\nof the locations of households',
    nami=="Proximity - jobs (%)" ~ 'Changes in spatial proximity to jobs: impact\nof the locations of jobs',
    TRUE ~ nami
    )

p<-result %>% 
  filter(match=='match_40',
         name==nami
         ) %>% 
  group_by(group) %>% 
  summarise(value=(prod(1+value/100))*100-100) %>% 
  ggplot(aes(x=group,y=value))+
  geom_bar(stat="identity", position=position_dodge(), aes(fill=group),show.legend = TRUE,width=0.6)+
  bbc_style()+
  #facet_wrap('name',scales='free')+
  theme(legend.position = "top", 
        legend.justification = "left",
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm")) +
  theme(
    legend.title = element_blank(),
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )+
  geom_hline(yintercept = 0000000, size = 1, colour="#333333") +
  labs(subtitle = "Accessibility gains per labor group, 1968-2010 (%)",title=nami2)

if (SAVE_ici) {
ggsave(paste0("./outputs/global",substr(nami,1,nchar(nami)-3),".png"),plot=p,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

plot(p)
}
```

# waterfall global

```{r}

result_df<-result %>% 
  filter(group=='group5') %>% 
  filter(name!='Real accessibility gains (%)') %>% 
  filter(match=="yes",transport=="TC") %>% 
  select(-c(match,transport,group))

result_df.tmp = result_df %>%
  #Set the factor levels in the order you want ----
  mutate(
    year = factor(year,levels = unique(result$year)),
    name = factor(name,levels = unique(result$name))
  ) %>%
  # \_Sort by Group and Category ----
  arrange(year, (value)) %>%
  ungroup() %>% 
  group_by(year) %>% 
  mutate(sum_pos=sum(ifelse(value>0,value,0)),
         #sum_neg=sum(ifelse(value<0,(value),0)),
         ) %>% 
  ungroup() %>% 
  # \_Get the start and end points of the bars ----
  mutate(sum_neg=cumsum(ifelse(value<0,(value),0)),
    cumsum_local=cumsum(abs(value)),
    end.Bar=sum_neg+cumsum_local,
         start.Bar = sum_neg + c(0, head(cumsum_local, -1))
         #start.Bar = c(0, head(end.Bar, -1))
         ) %>% 
  mutate(group.id = group_indices(., year)) %>% 
  mutate(name2=ifelse(value>0,as.character(name),"Proximity (negative %)"))


  # # \_Get numeric index for the groups ----
  # mutate(group.id = group_indices(., year)) %>%
  # # \_Create new variable with total by group ----
  # group_by(year) %>%
  # mutate(total.by.x = sum(value)) %>%
  # # \_Order the columns ----
  # select(year, name, group.id, start.Bar, value, end.Bar, total.by.x)

ggplot(result_df.tmp, aes( x = year, fill = name2)) + 
  # Waterfall Chart
  geom_rect(aes(x = year,
                xmin = group.id - 0.35, # control bar gap width
                xmax = group.id + 0.35, 
                ymin = end.Bar,
                ymax = start.Bar),
              color="black", 
            alpha=0.95)+
  geom_segment(aes(x=ifelse(group.id == last(group.id),
                            last(group.id),
                            group.id+0.25), 
                   xend=ifelse(group.id == last(group.id),
                               last(group.id),
                               group.id+0.75), 
                   y=ifelse(name == "job growth (%)",
                            end.Bar,
                            # these will be removed once we set the y limits
                            max(end.Bar)*2), 
                   yend=ifelse(name == "job growth (%)",
                               end.Bar,
                               # these will be removed once we set the y limits
                               max(end.Bar)*2)), 
               colour="black",linetype=2) +
  # \_Numbers inside bars (each category) ----
  geom_text(
    mapping = 
      aes(
        label = ifelse(value < 150, 
                       "",
                       ifelse(nchar(value) == 3,
                              as.character(value),
                              sub("(.{1})(.*)", "\\1.\\2", 
                                  as.character(value)
                              )
                            )
                       ),
        y = rowSums(cbind(start.Bar,value/2))
        ),
    color = "white",
    fontface = "bold"
    ) + 
  bbc_style()+
  ylim(-20,150)+
  #facet_wrap('group')+
  theme(legend.position = "top", 
        legend.justification = "left",
        #axis.ticks.x = element_line(colour = "#333333"), 
        #axis.ticks.length =  unit(0.26, "cm"),
        axis.text.x = element_text(angle=0,size=16),
        ) +
  theme(
    #legend.title = groupi,
    # panel.border = element_blank(),
    # panel.background = element_blank(),
    # strip.background = element_blank(),
  )

p



```

```{r}
result_df.tmp <- result_df %>%
  mutate(
    year = factor(year,levels = unique(result$year)),
    name = factor(name,levels = unique(result$name))
  ) %>%
  arrange(year, (value)) %>%
  ungroup() %>% 
  group_by(year)%>% 
  mutate(sum_pos=sum(ifelse(value>0,value,0)),
         sum_neg=sum(ifelse(value<0,abs(value),0)),
         cumsum_local=cumsum(abs(value)) %>% 
  ungroup()
  
  
  %>% 
  mutate(end.Bar=cumsum(value),
         start.Bar = c(0, head(end.Bar, -1))-sum_neg
         #start.Bar = c(0, head(end.Bar, -1))
         ) 
```


