---
title: "Graphs of the article"
format: html
---

# libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo = FALSE,warning = FALSE, message=FALSE)
library(tidyverse)
library(ncdf4)
library(stars)   
library(purrr)
library(dplyr)
library(readxl)
library(arrow)
library(ggspatial)
library(scales)
library(gtools)

# install.packages('devtools')
#devtools::install_github('bbc/bbplot')
library('bbplot')
```


# load data

## load data t night


```{r}
files <- list.files("./data/NFR010D/",
                    pattern = "^tn",
                    full.names = TRUE)
NFR010D <- map_dfr(files, ~ read_ncdf(.x) %>% as.data.frame())

files <- list.files("./data/NFR010C/",
                    pattern = "^tn",
                    full.names = TRUE)
NFR010C <- map_dfr(files, ~ read_ncdf(.x) %>% as.data.frame())

# write_parquet(NFR010C,"./data/NFR010C.parquet")
# write_parquet(NFR010D,"./data/NFR010D.parquet")
# 
# NFR010C <- read_parquet("./data/NFR010C.parquet")
# NFR010D <- read_parquet("./data/NFR010D.parquet")
```




## load population data


```{r}

df2 <- read_excel("./data/pop_sexe_age_communes_1990.xlsx") %>% 
  na.omit() #sinon ca rajoute plein de ligne vides avec des NA, qui posent pb ensuite
df3 <- read_excel("./data/pop_sexe_age_communes_2018.xlsx") %>% 
  na.omit()

sum_cols <- function(df, cols) {
  df %>%
    mutate(val = rowSums(select(., all_of(cols)), na.rm = TRUE)) %>%
    pull(val)
}

dic_age_df2 <- list(
  "65-H" = c("ageq_rec01s1rpop1990","ageq_rec02s1rpop1990","ageq_rec03s1rpop1990",
             "ageq_rec04s1rpop1990","ageq_rec05s1rpop1990","ageq_rec06s1rpop1990",
             "ageq_rec07s1rpop1990","ageq_rec08s1rpop1990","ageq_rec09s1rpop1990",
             "ageq_rec10s1rpop1990","ageq_rec11s1rpop1990","ageq_rec12s1rpop1990",
             "ageq_rec13s1rpop1990"),
  "65+H" = c("ageq_rec14s1rpop1990","ageq_rec15s1rpop1990","ageq_rec16s1rpop1990",
             "ageq_rec17s1rpop1990","ageq_rec18s1rpop1990","ageq_rec19s1rpop1990",
             "ageq_rec20s1rpop1990"),
  "65-F" = c("ageq_rec01s2rpop1990","ageq_rec02s2rpop1990","ageq_rec03s2rpop1990",
             "ageq_rec04s2rpop1990","ageq_rec05s2rpop1990","ageq_rec06s2rpop1990",
             "ageq_rec07s2rpop1990","ageq_rec08s2rpop1990","ageq_rec09s2rpop1990",
             "ageq_rec10s2rpop1990","ageq_rec11s2rpop1990","ageq_rec12s2rpop1990",
             "ageq_rec13s2rpop1990"),
  "65+F" = c("ageq_rec14s2rpop1990","ageq_rec15s2rpop1990","ageq_rec16s2rpop1990",
             "ageq_rec17s2rpop1990","ageq_rec18s2rpop1990","ageq_rec19s2rpop1990",
             "ageq_rec20s2rpop1990")
)

for (name in names(dic_age_df2)) {
  df2[[name]] <- sum_cols(df2, dic_age_df2[[name]])
}

df2 <- df2 %>%
  mutate(
    `65+` = `65+H` + `65+F`,
    `65-` = `65-H` + `65-F`
  )

# Harmonisation communes
com_equi <- read_csv("./data/corresp.csv")

for (i in com_equi$old_code) {
  target <- com_equi %>% filter(old_code == i) %>% pull(new_code)
  
  df2[df2$INSEE == target, c("65+","65-","65+H","65+F","65-H","65-F")] <-
    df2[df2$INSEE == target, c("65+","65-","65+H","65+F","65-H","65-F")] +
    df2[df2$INSEE == i, c("65+","65-","65+H","65+F","65-H","65-F")]
  
  df2 <- df2 %>% filter(INSEE != i)
}

df2 <- df2 %>%
  mutate(popTOT = `65+` + `65-`)


dic_age_df3 <- list(
  "65+H" = c("SEXE1_AGEPYR1065","SEXE1_AGEPYR1080"),
  		
  "65+F" = c("SEXE2_AGEPYR1065","SEXE2_AGEPYR1080"),
  "65-H" = c("SEXE1_AGEPYR1000","SEXE1_AGEPYR1003","SEXE1_AGEPYR1006","SEXE1_AGEPYR1011","SEXE1_AGEPYR1018","SEXE1_AGEPYR1025","SEXE1_AGEPYR1040","SEXE1_AGEPYR1055"),
  "65-F" = c("SEXE2_AGEPYR1000","SEXE2_AGEPYR1003","SEXE2_AGEPYR1006","SEXE2_AGEPYR1011","SEXE2_AGEPYR1018","SEXE2_AGEPYR1025","SEXE2_AGEPYR1040","SEXE2_AGEPYR1055")
)

for (name in names(dic_age_df3)) {
  df3[[name]] <- sum_cols(df3, dic_age_df3[[name]])
}

df3 <- df3 %>%
  mutate(
    `65+` = `65+H` + `65+F`,
    `65-` = `65-H` + `65-F`
  ) %>% 
  mutate(popTOT = `65+` + `65-`)


# fractions
df2 <- df2 %>%
  mutate(frac_age = `65+` / popTOT)

df3 <- df3 %>%
  mutate(frac_age = `65+` / popTOT)

# df2 <- df2 %>%
#   mutate(
#     `65+_inv` = popTOT * df3$frac_age_18,
#     `65-_inv` = popTOT * (1 - df3$frac_age_18)
#   )
# 
# df3 <- df3 %>%
#   mutate(
#     `65+_inv` = popTOT * df2$frac_age_90,
#     `65-_inv` = popTOT * (1 - df2$frac_age_90)
#   )

df2_join <- df2 %>% 
  select(INSEE,`65-H`,`65+H`,`65-F`,`65+F`,`65+`,`65-`,`popTOT`,`frac_age`) %>% 
  rename_with( ~paste0(.,"_90"), 2:9)

df3_join <- df3 %>% 
  select(CODGEO,`65-H`,`65+H`,`65-F`,`65+F`,`65+`,`65-`,`popTOT`,`frac_age`) %>% 
  rename_with( ~paste0(.,"_18"), 2:9) 
  
populations <- df2_join %>% 
  left_join(df3_join,by = c("INSEE" = "CODGEO"))

```

## compile all data

```{r}

nuit_trop_COM_NFR010D <- NFR010D %>%
  mutate(year = year(date)) %>%
  group_by(year,COM) %>%
  summarise(nb_nuit_trop_D = sum(tn > 20, na.rm = TRUE),
            nb_nuit_trop_D_18 = sum(tn > 18, na.rm = TRUE),
            nb_nuit_trop_D_19 = sum(tn > 19, na.rm = TRUE),
            nb_nuit_trop_D_21 = sum(tn > 21, na.rm = TRUE),
            nb_nuit_trop_D_22 = sum(tn > 22, na.rm = TRUE),
            nb_nuit_trop_D_25 = sum(tn > 25, na.rm = TRUE),
            nb_nuit_trop_D_32 = sum(tn > 32, na.rm = TRUE)) %>% 
  mutate(COM = as.character(COM))

nuit_trop_COM_NFR010C <- NFR010C %>%
  mutate(year = year(date)) %>%
  group_by(year,COM) %>%
  summarise(nb_nuit_trop_C = sum(tn > 20, na.rm = TRUE),
            nb_nuit_trop_C_18 = sum(tn > 18, na.rm = TRUE),
            nb_nuit_trop_C_19 = sum(tn > 19, na.rm = TRUE),
            nb_nuit_trop_C_21 = sum(tn > 21, na.rm = TRUE),
            nb_nuit_trop_C_22 = sum(tn > 22, na.rm = TRUE),
            nb_nuit_trop_C_25 = sum(tn > 25, na.rm = TRUE),
            nb_nuit_trop_C_32 = sum(tn > 32, na.rm = TRUE)) %>% 
  mutate(COM = as.character(COM))




shapefile2 <- shapefile %>%
  left_join(populations, by = c("INSEE_COM" = "INSEE")) %>% 
  left_join(nuit_trop_COM_NFR010D, by = c("INSEE_COM" = "COM"))%>% 
  left_join(nuit_trop_COM_NFR010C, by = c("INSEE_COM" = "COM","year" = "year")) 

font <- "arial" 

tmp <- shapefile2 %>%
  filter(year %in% (2002:2022)) %>% 
  group_by(geometry) %>% 
  summarise(nb_nuit_trop = (sum(nb_nuit_trop_D) - sum(nb_nuit_trop_C) ) ) 

plot(tmp)

write_parquet(shapefile2 %>% st_drop_geometry(),"./data/final_data.parquet")

final_data <- read_parquet("./data/final_data.parquet")
```


# graphs of section methods

## Number of tropical nights per year 
```{r}
p<- NFR010C %>% 
  #filter(COM %in% seq(75101,75111)) #%>% 
  filter(COM %in% seq(75101,75120))%>% 
  group_by(date) %>%
  summarise(tn = mean(tn)) %>% 
  mutate(year = year(date),
         month = month (date)) %>%
 # filter(year %in% c(2017,2018,2019,2020,2021,2022),
#         month %in% c(6,7,8,9)) %>% 
  filter(tn>=20)%>% 
  group_by(year) %>%
  summarise(nombre=n()) %>% 
  ggplot(aes(x=year,y=nombre))+
  geom_col(fill= "#1380A1")+
  #geom_point()+
  geom_hline(yintercept = 0)+
    bbc_style()+
  theme(
    axis.ticks.x = element_line(colour = "#333333"), 
    axis.ticks.length =  unit(0.26, "cm"),
  )+
  ggtitle("Total number of tropical nights in Paris",subtitle = "Number of tropical nights (>20°C) per year")
  
ggsave(paste0("./outputs/number_trop_paris.png"),plot=p,
       width = 2666/280,
       height= 1875/280,
       unit="in")

p
```

## Daily minimal temperatures in Paris


```{r}
tmp <- NFR010C %>% 
  #filter(COM %in% seq(75101,75111)) #%>% 
  filter(COM %in% seq(75101,75120))%>% 
  group_by(date) %>%
  summarise(tn = mean(tn)) %>% 
  mutate(year = year(date),
         month = month (date)) %>%
  filter(year %in% c(2017,2018,2019,2020,2021,2022),
         month %in% c(6,7,8,9)) %>% 
  mutate(tn_bis = if_else(tn>=20,tn,20))

tmp2 <- NFR010C %>% 
  #filter(COM %in% seq(75101,75111)) #%>% 
  filter(COM %in% seq(75101,75120))%>% 
  group_by(date) %>%
  summarise(tn = mean(tn)) %>% 
  mutate(year = year(date),
         month = month (date)) %>%
 # filter(year %in% c(2017,2018,2019,2020,2021,2022),
#         month %in% c(6,7,8,9)) %>% 
  filter(tn>=20)%>% 
  group_by(year) %>%
  summarise(nombre=n()) 


p <- tmp %>% 
  left_join(tmp2,by = join_by(year == year) ) %>% 
  mutate(year = paste0(year,"\n(",nombre," tropical nights)")) %>% 
  ggplot(aes(x=date,y=tn))+
  geom_line()+
  #geom_line(aes(y=tn_bis),color="red")+
  geom_hline(aes(yintercept = 20),linetype = "dotted")+
  facet_wrap(~year,scales = "free_x")+
  bbc_style()+
  theme(
    axis.ticks.x = element_line(colour = "#333333"), 
    axis.ticks.length =  unit(0.26, "cm"),
  )+
  ggtitle("Daily minimal temperatures in Paris (°C)")

ggsave(paste0("./outputs/night_temp_paris.png"),plot=p,
       width = 2666/230,
       height= 1875/230,
       unit="in")
p
```


## map of evolution of population


```{r}

tmp <- final_data %>% 
  filter(year %in% c(2019))

tmp2 <- shapefile %>% 
  dplyr::select (c(INSEE_COM,geometry)) %>% 
  left_join(tmp,by =c("INSEE_COM" = "INSEE_COM") ) %>% 
  mutate(diff= (`65+_18` - `65+_90`))
  
#st_write(tmp2, "commune_pour_carte.shp")


p <- tmp2 %>% 
  ggplot()+
  geom_sf(aes(fill = diff),color="grey50",size=.2)+
  scale_fill_distiller(palette = "PuOr",
                       #limits = c(-max(abs(tmp2$diff)),max(abs(tmp2$diff))),
                       limits = c(-10000,10000),
                       breaks = c(-10000,-5000,0,5000,10000))+
  #geom_sf(aes(fill = tn),lwd=0)+
  bbc_style()+
  annotation_scale(location = "bl", width_hint = 0.25) +
  annotation_north_arrow(location = "br", which_north = "true", 
                         #pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "right")+
  ggtitle("Variation in population aged 65+ in each Commune",subtitle = "Evolution between 1990 and 2018")

p

ggsave(paste0("./outputs/map_population_65_evolution.png"),plot=p,
       width = 2666/280*1.5,
       height= 1875/280,
       unit="in")
```

# Background functions to compute waterfall graphs

### function which computes the waterfall graph

```{r}


draw_waterfall <- function(shapley_df = shapley_df,df = df,vars = c("LULC", "AGE", "POP"),start_val = 90, end_val = 18,title_ici ="Change in population exposed to heat",subtitle_ici = "Thousands of people, age 65+, Tn > 15°C",put_rect_text_outside_when_value_below = 27)
{
  # =========================
# VALUE FUNCTION
# =========================

get_value <- function(state) {
  
  conds <- Map(function(var) {
    df[[var]] == state[[var]]
  }, vars)
  
  rows <- Reduce(`&`, conds)
  
  val <- df$value[rows]
  
  if (length(val) != 1) {
    stop("State not uniquely matched")
  }
  
  return(val)
}

# =========================
# ALL PERMUTATIONS
# =========================
k <- length(vars)

# =========================
# START / END VALUES
# =========================
v_start <- get_value(setNames(rep(start_val, k), vars))
v_end   <- -get_value(setNames(rep(end_val, k), vars))


wf <- data.frame(
  step = c("If population\nand land use\nas in 1990", shapley_df$variable, "If population\nand land use\nas in 2018"),
  value = c(v_start, shapley_df$shapley, v_end),
  type = c("total", rep("change", k), "total")
)


levels <- wf$step

# =========================
# SETUP for graph
# =========================
data1 <- wf  %>%
    mutate(step = factor(step, levels = levels),
        ymin = round(cumsum(value),  length(vars)),
        ymax = lag(cumsum(value), default = 0),
        xmin = c(head(step, -1), NA),
        xmax = c(tail(step, -1), NA),
        Impact = ifelse(step %in% c(as.character(wf$step[1]), as.character(wf$step[nrow(wf)])),"Budget",
                        ifelse(value > 0, "Increase", "Decrease")
           )) %>% 
  mutate(ymin=ymin/1000,
         ymax = ymax /1000) %>% 
  mutate(step2 = as.factor(case_when(
          # step == "LULC" ~ "impact of\nland-use change\non urban climate",
          # step == "year" ~ "climate change",
          # step == "AGE" ~ "change in the ratio\nof people aged 65+\nin the population",
          # step == "POP" ~ "change in the\nlocation of people\naged 65+ within\nthe region",
          # step == "REP" ~ "global population\nincrease in the\nregion",
          # step == "REP_age" ~ "change in the ratio\nof people aged 65+\nin the population",
          step == "LULC" ~ "Land-use change\n(urban\nclimate)",
          step == "year" ~ "Climate change",
          step == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
          step == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
          step == "REP" ~ "Total population\nincrease",
          step == "REP_age" ~ "Population\nage structure",
        TRUE ~ step)))

# =========================
# WATERFALL PLOT
# =========================

w <- 0.7  #use to set width of bars

g <- data1 %>% 
  mutate(label_ici = round(ymin-ymax)) %>% 
  mutate(label_ici = if_else(step == "If population\nand land use\nas in 2018",-label_ici,label_ici)) %>% 
  ggplot() +
    geom_rect(aes(xmin = as.integer(step) - w/2,
                  xmax = as.integer(step) + w/2, ymin = ymin, ymax = ymax,
                  fill = Impact), colour = "black") +
    scale_x_discrete(labels =data1$step2 ,limits = levels) +
    scale_fill_manual(values = (c("Decrease" = "#FAAB18",  "Increase" = "#1380A1" , "Budget" = "black"))) +
  geom_segment(data = data1[1:(nrow(data1) -1),],
               aes(x = xmin,
                   xend = xmax,
                   y = ymin,
                   yend = ymin),
               linetype="dashed")+
  geom_text(aes(x = as.integer(step) ,
                y = if_else(abs(ymin-ymax)> put_rect_text_outside_when_value_below,
                            ymin /2 + ymax /2,
                           ymin /2 + ymax /2- put_rect_text_outside_when_value_below
                            ), 
                label = label_ici,
                color = abs(ymin-ymax)< put_rect_text_outside_when_value_below #(Impact != "Budget")
                                ),
            size=7)+
  scale_color_manual(values = c("white","black"))+
  bbc_style()+
   theme(legend.position = "none",
         axis.text.x = element_text(angle=0,size=16),) +
    ggtitle(title_ici,
          subtitle = subtitle_ici)+
  geom_hline(yintercept =0)

return(g)

#write.csv(perm_df, "permutation_contributions.csv", row.names = FALSE)
#write.csv(shapley_df, "shapley_values.csv", row.names = FALSE)
}

```

### function which computes shapley values

```{r}
compute_permut <- function(df,vars = c("LULC", "AGE", "POP"),start_val = 90, end_val = 18)
{
  # =========================
# VALUE FUNCTION
# =========================

get_value <- function(state) {
  
  conds <- Map(function(var) {
    df[[var]] == state[[var]]
  }, vars)
  
  rows <- Reduce(`&`, conds)
  
  val <- df$value[rows]
  
  if (length(val) != 1) {
    stop("State not uniquely matched")
  }
  
  return(val)
}

# =========================
# ALL PERMUTATIONS
# =========================
k <- length(vars)
perms <- permutations(k, k, vars)

# =========================
# PATH DECOMPOSITION
# =========================
decompose_path <- function(order) {
  
  state <- setNames(rep(start_val, k), vars)
  prev <- get_value(state)
  
  out <- list()
  
  for (i in seq_along(order)) {
    
    var <- order[i]
    state[var] <- end_val
    
    new <- get_value(state)
    
    out[[i]] <- data.frame(
      permutation = paste(order, collapse = "→"),
      variable = var,
      contribution = new - prev
    )
    
    prev <- new
  }
  
  bind_rows(out)
}

# =========================
# ALL PERMUTATION CONTRIBUTIONS
# =========================
perm_df <- bind_rows(lapply(1:nrow(perms), function(i) {
  decompose_path(perms[i, ])
}))


perm_df <- map_dfr(1:nrow(perms), ~ decompose_path(perms[.x, ]))


return(perm_df)

#write.csv(perm_df, "permutation_contributions.csv", row.names = FALSE)
#write.csv(shapley_df, "shapley_values.csv", row.names = FALSE)
}
```



# results

## cumulative graph

```{r}


# Reshape to long format
df_long <- final_data %>%
  filter(year %in% c(2017,2018,2019,2020,2021,2022)) %>% 
  dplyr::select(`65+_90`,`65+_18`,nb_nuit_trop_C,nb_nuit_trop_D,year,INSEE_COM) %>% 
  rename("pop_1990" = "65+_90",
         "pop_2018" = "65+_18",
         "hot_days_1990" = "nb_nuit_trop_C",
         "hot_days_2018" = "nb_nuit_trop_D") %>% 
  pivot_longer(
    cols = c(pop_1990, pop_2018, hot_days_1990, hot_days_2018),
    names_to = c(".value", "scenario"),
    names_pattern = "(.+)_(1990|2018)"
  ) %>%
  rename(population = pop, hot_days = hot_days) %>%
  mutate(scenario = paste("If population and land use\nwere as in", scenario))

# For each hot_days threshold, compute cumulative population exceeding it
hot_day_vals <- sort(unique(df_long$hot_days))

cumulative_df <- df_long %>%
  group_by(scenario,year) %>%
  reframe(
    hot_days_threshold = hot_day_vals,
    cum_pop = sapply(hot_day_vals, function(x) {
      sum(population[hot_days >= x])
    })
  )

cumulative_df %>% filter(hot_days_threshold ==1)
cumulative_df %>% filter(hot_days_threshold ==11) %>% 
  pivot_wider(names_from = scenario, values_from = cum_pop) %>% 
  mutate(ratio = `If population and land use\nwere as in 2018`/`If population and land use\nwere as in 1990`)

# Plot
p <- ggplot(cumulative_df, aes(x = hot_days_threshold, y = cum_pop / 1e6, color = scenario, fill = scenario)) +
  geom_step(linewidth = 1) +
  labs(
    title = "Cumulative population aged  65 years and over\nexposed to at least X tropical nights",
    x = "Number of tropical nights (threshold)",
    y = "Cumulative population (millions)",
    color = "",
    fill = ""
  ) +
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0)+
  facet_wrap(~ year) +
  bbc_style()+
  theme(
    axis.ticks.x = element_line(colour = "#333333"),
    axis.ticks.length =  unit(0.26, "cm"),
    legend.position = "top", 
    legend.justification = "left",
    #axis.ticks.x = element_line(colour = "#333333"), 
    #axis.ticks.length =  unit(0.26, "cm"),
    axis.title = element_text(angle=0,size=16),
    panel.grid.major.x = element_line(color="#cbcbcb"), 
  )
p
  # theme_minimal(base_size = 18) +
  # theme(legend.position = "top")

ggsave(paste0("./outputs/par_canicule/cumulative.png"),plot=p,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```

## graph for each year and each threshold

Here, to change the temperature threshold, change the variables `nb_nuit_trop_C` and `nb_nuit_trop_D` by `nb_nuit_trop_C_18` and `nb_nuit_trop_D_18` to use 18°C as a threshold, `nb_nuit_trop_C_19` and `nb_nuit_trop_D_19` to use 19°C as a threshold etc.

```{r, warnings=False }


memoire_df <- data_frame()
for (year_ici in c(2017,2018,2019,2020,2021,2022))
{

  for (seuil in seq(3,12))
  {
    
    tmp <- final_data %>% 
      filter(year == year_ici)
    
    df <- final_data %>% 
      filter(year == year_ici) %>% 
      mutate(seuil_18 = nb_nuit_trop_D >seuil,
             seuil_90 = nb_nuit_trop_C > seuil) %>% 
      group_by(year,INSEE_COM) %>% 
      summarise(
        LULC90_POP90 = sum( `65+_90` * seuil_90 ),
        LULC90_POP18 = sum( `65+_18` * seuil_90 ),
        LULC18_POP90 = sum( `65+_90` * seuil_18 ),
        LULC18_POP18 = sum( `65+_18` * seuil_18 ),
        .groups = "drop_last"
      ) %>% 
      pivot_longer(cols=-c(year,INSEE_COM)) %>% 
      separate_wider_delim(cols = name,delim="_",names = c("LULC","POP")) %>% 
      separate_wider_position(LULC,widths = c( 4,LULC = 2)) %>% 
      separate_wider_position(POP,widths = c( 3,POP = 2)) %>% 
      group_by(,LULC,POP) %>% 
      summarise(value=sum(value),.groups = "drop_last")
    
    pop_totale_tmp <- final_data %>% 
      filter(year == 2020) %>% #peu importe, c'est juste pour ne garder qu'une année
      ungroup() %>% 
      summarise(
        pop_totale_1990 = sum(popTOT_90),
        pop_totale_2018 = sum(popTOT_18),
        pop_65_1990 = sum(`65+_90`),
        pop_65_2018 = sum(`65+_18`),
      )
    
    ratio_65_1990 = pop_totale_tmp$pop_65_1990/pop_totale_tmp$pop_totale_1990 
    ratio_65_2018 = pop_totale_tmp$pop_65_2018/pop_totale_tmp$pop_totale_2018 
    
    df2<- df %>% 
      mutate(REP = 90,
             value=if_else(POP==18,value * pop_totale_tmp$pop_totale_1990/pop_totale_tmp$pop_totale_2018,value))
    
    df3 <- df %>% 
      mutate(REP = 18, 
             value=if_else(POP==90,value * pop_totale_tmp$pop_totale_2018/pop_totale_tmp$pop_totale_1990,value))
    
    df_tmp <- rbind(df2,df3)
    
    df2<- df_tmp %>% 
      mutate(REP_age = 90,
             value=if_else(POP==18,value*ratio_65_1990/ratio_65_2018,value))
    
    df3 <- df_tmp %>% 
      mutate(REP_age = 18, 
             value=if_else(POP==90,value*ratio_65_2018/ratio_65_1990,value))
    
    df_tmp <- rbind(df2,df3) %>% 
      dplyr::select("REP","REP_age" ,"POP" ,"LULC","value") 
    
    perm_df <- compute_permut(df_tmp,vars = c(  "REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18) #"AGE",
    
    shapley_df <- perm_df %>%
      group_by(variable) %>%
      summarise(
        shapley = mean(contribution),
        .groups = "drop"
      ) %>% 
      mutate(ordre=factor(variable,levels = c("REP","REP_age", "POP","LULC")))
    
    min_max <- perm_df %>% 
      group_by(variable) %>% 
      summarise(mini = min(contribution),
                maxi = max(contribution),
                quant75 = quantile(contribution,probs = 0.75),
                quant25 = quantile(contribution,probs = 0.25))
    
    #variable qui stocke les resultats du shapley
    memoire_df <- shapley_df %>% 
      dplyr::select(-variable) %>% 
      mutate(year = year_ici,
             seuil = seuil) %>% 
      left_join(min_max,by = c("ordre" = "variable")) %>% 
      rbind(memoire_df) 
      
    
    if (draw_ici) 
    {
      g <- draw_waterfall(shapley_df,df_tmp,vars = c("REP",  "POP","LULC","REP_age"),start_val = 90, end_val = 18,title = paste0(year_ici," summer, number of people exposed to\nmore than ",seuil," tropical nights"),  subtitle = "Thousands of people, age 65+",put_rect_text_outside_when_value_below = 80)
      g
      
      h <- perm_df %>% 
        mutate(variable = as.factor(case_when(
          # variable == "LULC" ~ "impact of\nland-use change\non urban climate",
          # variable == "year" ~ "climate change",
          # variable == "AGE" ~ "change in the ratio\nof people aged 65+\nin the population",
          # variable == "POP" ~ "change in the\nlocation of people\naged 65+ within\nthe region",
          # variable == "REP" ~ "global population\nincrease in the\nregion",
          # variable == "REP_age" ~ "change in the ratio\nof people aged 65+\nin the population",
          variable == "LULC" ~ "Land-use change\n(urban\nclimate)",
          variable == "year" ~ "Climate change",
          variable == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
          variable == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
          variable == "REP" ~ "Total population\nincrease",
          variable == "REP_age" ~ "Population\nage structure",
          TRUE ~ variable))) %>% 
        ggplot(aes(x=variable,y=contribution/1000))+
        geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
        #geom_boxplot(alpha=0.,outlier.shape = NA)+
        bbc_style()+
        theme(legend.position = "none",
              axis.text.x = element_text(angle=0,size=16),) +
        ggtitle("Influence of each variable, for all permutations",
                subtitle = paste0(year_ici," summer, thousands of people, age 65+,\nexposed to more than ",seuil," tropical nights"))+
        geom_hline(yintercept =0)
      
      h
      
      ggsave(paste0("./outputs/par_canicule/canicule_",year_ici,"_",seuil,".png"),plot=g,
             width = 2666/250,
             height= 1875/250,
             unit="in")
      
      ggsave(paste0("./outputs/par_canicule/distrib_canicule_",year_ici,"_",seuil,".png"),plot=h,
             width = 2666/250,
             height= 1875/250,
             unit="in")
    }
  }
}

write_parquet(memoire_df,"./data/memoire_df.parquet")
```

## Summary graph

```{r}

memoire_df <- read_parquet("./data/memoire_df.parquet")

g <- memoire_df %>% 
  mutate(ordre = case_when(
    ordre == "LULC" ~ "Land-use change\n(urban climate)",
    ordre == "year" ~ "Climate change",
    ordre == "AGE" ~ "Change in the ratio\nof people aged 65+\nin the population",
    ordre == "POP" ~ "Location of\npeople aged 65+\nwithin the region",
    ordre == "REP" ~ "Total population\nincrease",
    ordre == "REP_age" ~ "Population\nage structure",
    TRUE ~ ordre)) %>% 
  ggplot(aes(x=seuil,y=shapley,group=ordre,color=ordre,fill = ordre))+
  geom_line()+
  geom_ribbon(aes(ymin = mini, ymax = maxi),
              alpha = 0.3,
              color = NA) +
  facet_wrap(~year)+
  geom_hline(yintercept = 0)+
  bbc_style()+
  labs(x="Number of tropical nights",y="Change in number of people 65+\nexposed to persistent\ntropical-night exposure")+
  ggtitle("Evolution of the contribution of each variable",
          subtitle = "When changing the number of tropical nights")+
  theme(axis.ticks.x = element_line(colour = "#333333"),
        axis.ticks.length =  unit(0.26, "cm"),
        axis.title = ggplot2::element_text( size = 18, color = "#222222"))+
  scale_x_continuous(breaks = seq(3,12,))

g
ggsave(paste0("./outputs/par_canicule/summary.png"),plot=g,
       width = 2666/250,
       height= 1875/250,
       unit="in")
```