---
title: "analyse trade"
format: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo = FALSE,warning = FALSE, message=FALSE)

library(tidyverse)
library(readxl)
library(readr)
library(pacman)
library(shadowtext)
library(ggrepel)
library(sf)
library("rnaturalearth")
library("rnaturalearthdata")
library(viridis)
library(metR)
library(ggnewscale)
library(maps)
library(RColorBrewer)
library(forcats)
  library("rnaturalearthdata")
  library(raster)
  library("sf")
  library(stringr)
  library(cowplot)
  library(dbplyr)
  library(dplyr)
  library(grid) # for unit
  library(gridExtra) # for grid.arrange
  libs <- c("rgdal", "maptools", "gridExtra")
  library(knitr)
  library(kableExtra)
  library(shadowtext)
  library(ggrepel)
    library(arrow)
  set.seed(42)
  lapply(libs, require, character.only = TRUE)
  library(ggExtra)
  library(scales)

# install.packages('devtools')
#devtools::install_github('bbc/bbplot')
library('bbplot')
  
#install.packages("ggmagnify", repos = c("https://hughjonesd.r-universe.dev", 
#                 "https://cloud.r-project.org"))

pacman::p_load('dplyr', 'tidyr', 'gapminder',
               'ggplot2',  'ggalt',
               'forcats', 'R.utils', 'png', 
               'grid', 'ggpubr', 'scales',
               'bbplot', 'ggalluvial','ggforce','ggmagnify')


SAVE_ici<-TRUE
SAVE_ici_bis<-FALSE

```

# chargement données

```{r load data}

final_dataframe                       = read_parquet("../data/final_dataframe.parquet")
final_dataframe_club_gdp_riskiest_2020= read_parquet("../data/final_dataframe_club_gdp_riskiest_2020.parquet")
final_dataframe_club_gdp_riskiest_2050= read_parquet("../data/final_dataframe_club_gdp_riskiest_2050.parquet")
final_dataframe_club_gdp_riskiest_2100= read_parquet("../data/final_dataframe_club_gdp_riskiest_2100.parquet")
final_dataframe_new                   = read_parquet("../data/final_dataframe_new.parquet")
final_dataframe_unif_2020             = read_parquet("../data/final_dataframe_unif_2020.parquet")
final_dataframe_unif_2050             = read_parquet("../data/final_dataframe_unif_2050.parquet")
final_dataframe_unif_2100             = read_parquet("../data/final_dataframe_unif_2100.parquet")


# correction adrien
# Annual values
cols_to_divide = c(
  'Initial capital loss (%)', 'Capital Damage ($ bn)', 'Capital Damage (%)',
  'Direct Production Loss ($ bn)', 'Direct Production Loss (%)',
  'Indirect Production Loss ($ bn)', 'Indirect Production Loss (%)',
  'Consumption Loss ($ bn)', 'Consumption Loss (%)',
  'Foreign Consumption Loss ($ bn)', 'Foreign Production Loss ($ bn)',
  'Foreign Production Loss (%)', 'Foreign Consumption Loss (%)',
  'Local Production Loss (%)', 'Total Production Loss (%)',
  'Total Consumption Loss (%)'
)

final_dataframe_unif_2020[,cols_to_divide] = final_dataframe_unif_2020[,cols_to_divide] / 10
final_dataframe_unif_2050[,cols_to_divide] = final_dataframe_unif_2050[,cols_to_divide] / 10
final_dataframe_unif_2100[,cols_to_divide] = final_dataframe_unif_2100[,cols_to_divide] / 10

final_dataframe_club_gdp_riskiest_2020[,cols_to_divide] = final_dataframe_club_gdp_riskiest_2020[,cols_to_divide] / 10
final_dataframe_club_gdp_riskiest_2050[,cols_to_divide] = final_dataframe_club_gdp_riskiest_2050[,cols_to_divide] / 10
final_dataframe_club_gdp_riskiest_2100[,cols_to_divide] = final_dataframe_club_gdp_riskiest_2100[,cols_to_divide] / 10


gdp_riskiest_aggregation<-read_csv("../data/gdp_riskiest_aggregation_2050.csv") %>% 
  mutate(`Trade Zone`=case_when(
    `Trade Zone` == "Low Risk" ~ "Low local flood risk",
    `Trade Zone` == "High Risk" ~ "High local flood risk"
  ))


results <- final_dataframe_unif_2050 %>% 
  separate_wider_delim(cols=Scenario,delim="_",names=c(NA,"base",NA,"future","SSP","trade")) %>% 
  mutate(base = substr(base, 6, nchar(base)),
         future = substr(future, 6, nchar(future)),
         SSP = substr(SSP, 5, nchar(SSP)),
         trade = substr(trade, 7, nchar(trade)),)

results2 <- final_dataframe_unif_2050 %>% mutate(climate=2050) %>% 
  rbind(final_dataframe_unif_2020 %>% mutate(climate=2020)) %>% 
  rbind(final_dataframe_unif_2100 %>% mutate(climate=2100))%>% 
  separate_wider_delim(cols=Scenario,delim="_",names=c(NA,"base",NA,"future","SSP","trade")) %>% 
  mutate(base = substr(base, 6, nchar(base)),
         future = substr(future, 6, nchar(future)),
         SSP = substr(SSP, 5, nchar(SSP)),
         trade = substr(trade, 7, nchar(trade)),)
  
results_club <- final_dataframe_club_gdp_riskiest_2050 %>% 
  separate_wider_delim(cols=Scenario,delim="_",names=c(NA,"base",NA,"future","SSP",NA,NA,NA,"trade")) %>% 
  mutate(base = substr(base, 6, nchar(base)),
         future = substr(future, 6, nchar(future)),
         SSP = substr(SSP, 5, nchar(SSP)),
         ) %>% 
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))

results2_club <- final_dataframe_club_gdp_riskiest_2050 %>% mutate(climate=2050) %>% 
  rbind(final_dataframe_club_gdp_riskiest_2020 %>% mutate(climate=2020)) %>% 
  rbind(final_dataframe_club_gdp_riskiest_2100 %>% mutate(climate=2100))%>% 
  separate_wider_delim(cols=Scenario,delim="_",names=c(NA,"base",NA,"future","SSP",NA,NA,NA,"trade")) %>% 
  mutate(base = substr(base, 6, nchar(base)),
         future = substr(future, 6, nchar(future)),
         SSP = substr(SSP, 5, nchar(SSP)),
         ) %>% 
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))

population<-read_excel("./data_vincent/API_SP.POP.TOTL_DS2_en_excel_v2_174095.xls",sheet="Data",skip=2) %>% 
  dplyr::select('Country Code','2024') %>% 
  rename('population_2024' = '2024') %>% 
  mutate(`Country Code`=case_when(
    `Country Code` == "SSD" ~"SDS",
    `Country Code` == "SDN" ~"SUD",
    TRUE ~ `Country Code`
  )) 

population[nrow(population) + 1,] = list("ANT",1000000)# pas sûr du chuffre, mais ça doit être aux environs de ça
population[nrow(population) + 1,] = list("TWN",23588613)


tmp <- results %>% 
  left_join(population, by=c("Country" = "Country Code"))

region <- read_tsv("./data_vincent/region_classification.tsv") %>% 
  mutate(ISO=case_when(
    ISO == "SSD" ~"SDS",
    ISO == "SDN" ~"SUD",
    TRUE ~ ISO
  )) 

```

# figure Adrien


## figure 2
```{r figure 2}

results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade == "constant") %>%
  mutate(`Local Consumption Loss (%)`= `Total Consumption Loss (%)` - `Foreign Consumption Loss (%)`) %>% 
  mutate(`Local Consumption Loss (%)` = `Local Consumption Loss (%)`,
         `Consumption Loss (%)` = `Consumption Loss (%)`,
         `Foreign Consumption Loss (%)` = `Foreign Consumption Loss (%)`) %>% 
  filter(`Total Consumption Loss (%)`>10^-2) %>%
  ggplot(aes(y=`Foreign Consumption Loss (%)`,x=`Local Consumption Loss (%)` ))+
  geom_point(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  geom_hline(yintercept=0)+
  bbc_style()+
  #ggtitle(str_wrap("Total consumption loss",40))+
  theme(axis.title = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(transform="log",#scales::pseudo_log_trans(base = 10),
                     labels = function(x) sprintf("%g %%", x),
                     #breaks = c(0, 0.5,1,2,3,5,10,15),
                     "Consumption losses due to local floods")+
  scale_color_manual(values = c( "#DC3220","#005AB5"))+
  scale_y_continuous(transform="log",#scales::pseudo_log_trans(base = 10),
                     labels = function(x) sprintf("%g %%", x),
                     #breaks = c(0, 0.5,1,2,3,5,10,15),
                     "Consumption losses due to foreign floods")
  
  



```
## figure 3
### figure 3 capital
```{r figure 3}
tmp <- results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade == "constant") %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`,
         `Initial capital loss (%)` = `Initial capital loss (%)`) %>% 
  filter(`Total Consumption Loss (%)`>10^-2) %>%
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code")) %>% 
  dplyr::select(`Total Consumption Loss (%)`,`Initial capital loss (%)` ,`Trade Zone`,Country) %>% 
  left_join(population, by=c("Country" = "Country Code"))


p<-tmp %>% 
  mutate(`Trade Zone`=if_else(`Initial capital loss (%)` ==0,"Low local flood risk\n(No local floods)",`Trade Zone`)) %>% 
  ggplot(aes(y=`Total Consumption Loss (%)`/100,x=`Initial capital loss (%)`/100,color=`Trade Zone`))+
  geom_vline(xintercept=0)+
  geom_point(alpha=0.7,size=4)+ #fill="#1380A1",color="#1380A1"  aes(size=population_2024)
  geom_hline(yintercept=0)+
  bbc_style()+
  #ggtitle(str_wrap("Total consumption loss",40))+
  theme(axis.title = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(#transform="log10",#scales::pseudo_log_trans(base = 10),
                     labels = scales::percent,
                     #breaks = c(0.0001, 0.01,0.1,1,10),
                     "Capital losses due to local floods")+
  scale_color_manual(values = c( "#DC3220","#005AB5","grey70")) +
  scale_y_continuous(#transform="log",#scales::pseudo_log_trans(base = 10),
                     labels = scales::percent,
                     #breaks = c(0, 0.5,1,2,3,5,10,15),
                     "Total consumption loss")+
  geom_vline(xintercept=(0.5428833+0.5423993)/2/100,linetype="dashed",size=0.1,alpha=0.9)+
  guides(size = "none")+
  ggtitle("a) Capital losses and total consumption losses")
  #scale_size_area(max_size = 10)
p
q<-ggMarginal(p,margins = 'y',groupFill = FALSE,,type = "histogram")
  
#transform = scales::transform_pseudo_log(base = 10)
q


xlim_from <- c(0, 0.4)/100
ylim_from <- c(0, 3)/100
xlim_to <- c(4,8.5)/100
ylim_to <- c(1,10.5)/100

# Create the zoomed-in plot
zoom_plot <- p +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    title = element_blank(),
    axis.text = element_text(size = 12),
    plot.background = element_rect(fill = "white", color = "black"),
    legend.position = "none",
  )+
  scale_x_continuous(labels = scales::percent,
                     limits = xlim_from,
                     #breaks = c(0,0.005,0.01)
                     )+
  scale_y_continuous(labels = scales::percent,
                     limits = ylim_from,
                     #breaks = c(0,0.05)
                     )


q2<-p + annotation_custom(
    grob = ggplotGrob(zoom_plot), 
    xmin = xlim_to[1], xmax = xlim_to[2], 
    ymin = ylim_to[1], ymax = ylim_to[2]
  ) +
  annotate("rect", xmin = xlim_from[1], xmax = xlim_from[2], ymin = ylim_from[1], ymax = ylim_from[2], 
           color = "red", fill = NA, linetype = "dashed")

r<-ggMarginal(q2,margins = 'y',groupFill = FALSE,,type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig3.png"),plot=q2,
       width = 2666/400*2,
       height= 1875/400*1.5,
       unit="in")
}

xlim_from <- c(0, 0.4)/100
ylim_from <- c(0, 3)/100
xlim_to <- c(5,8.)/100
ylim_to <- c(1.5,10.5)/100

#from <- c(xmin = 0, xmax = 1, ymin = 0, ymax = 10)
#Names xmin, xmax, ymin, ymax are optional:
from <- c(xlim_from,ylim_from)
to <- c(xlim_to,ylim_to)
q2 <- p+ geom_magnify(from = from, to = to,
                  shadow = FALSE)

r<-ggMarginal(q2,margins = 'y',groupFill = FALSE,,type = "histogram")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig3_bis.png"),plot=q2,
       width = 2666/400*2,
       height= 1875/400*1.5,
       unit="in")
}

```

### figure 3 direct a
```{r figure 3}
tmp <- results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade == "constant") %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`,
         `Consumption Loss (%)` = `Consumption Loss (%)`) %>% 
  filter(`Total Consumption Loss (%)`>10^-2) %>%
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code")) %>% 
  dplyr::select(`Total Consumption Loss (%)`,`Initial capital loss (%)` ,`Trade Zone`,Country,`Consumption Loss (%)`) %>% 
  left_join(population, by=c("Country" = "Country Code"))


p<-tmp %>% 
  mutate(`Trade Zone`=if_else(`Initial capital loss (%)` ==0,"Low local flood risk\n(No local floods)",`Trade Zone`)) %>% 
  ggplot(aes(y=`Total Consumption Loss (%)`/100,x=`Consumption Loss (%)` /100,color=`Trade Zone`))+
  geom_vline(xintercept=0,size=0.3)+
  geom_hline(yintercept=0,size=0.3)+
  geom_point(alpha=0.7,size=3)+ #fill="#1380A1",color="#1380A1"  aes(size=population_2024)
  #ggtitle(str_wrap("Total consumption loss",40))+
  bbc_style()+
  theme(axis.title = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(labels = scales::percent,
                     "Capital losses due to local floods")+
  scale_color_manual(values = c( "#DC3220","#005AB5","grey70")) +
  scale_y_continuous(labels = scales::percent,
                     "Total consumption loss")+
  guides(size = "none")+
  ggtitle("a) Capital losses and total consumption losses")



xlim_from <- c(0, 0.75)/100
ylim_from <- c(0, 3)/100
xlim_to <- c(11,17.5)/100
ylim_to <- c(0.5,10.5)/100

# Create the zoomed-in plot
zoom_plot <- p +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    title = element_blank(),
    axis.text = element_text(size = 12),
    plot.background = element_rect(fill = "white", color = "black"),
    legend.position = "none",
  )+
  scale_x_continuous(labels = scales::percent,
                     limits = xlim_from,
                     #breaks = c(0,0.005,0.01)
                     )+
  scale_y_continuous(labels = scales::percent,
                     limits = ylim_from,
                     #breaks = c(0,0.05)
                     )


q<-p + annotation_custom(
    grob = ggplotGrob(zoom_plot), 
    xmin = xlim_to[1], xmax = xlim_to[2], 
    ymin = ylim_to[1], ymax = ylim_to[2]
  ) +
  annotate("rect", xmin = xlim_from[1], xmax = xlim_from[2], ymin = ylim_from[1], ymax = ylim_from[2], 
           color = "red", fill = NA, linetype = "dashed")
q

r<-ggMarginal(q,margins = 'y',groupFill = FALSE,,type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig3_direct.png"),plot=r,
       width = 2666/400*2,
       height= 1875/400,
       unit="in")
}

```

### figure 3 direct b
```{r figure 3}
tmp <- results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade == "constant") %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`,
         `Consumption Loss (%)` = `Consumption Loss (%)`) %>% 
  filter(`Total Consumption Loss (%)`>10^-2) %>%
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code")) %>% 
  dplyr::select(`Total Consumption Loss (%)`,`Initial capital loss (%)` ,`Trade Zone`,Country,`Consumption Loss (%)`) %>% 
  left_join(population, by=c("Country" = "Country Code"))


p<-tmp %>% 
  mutate(`Trade Zone`=if_else(`Initial capital loss (%)` ==0,"Low local flood risk\n(No local floods)",`Trade Zone`)) %>% 
  ggplot(aes(y=`Total Consumption Loss (%)`,x=`Consumption Loss (%)` ,color=`Trade Zone`))+
  #geom_vline(xintercept=0)+
  geom_point(alpha=0.7,size=4)+ #fill="#1380A1",color="#1380A1"  aes(size=population_2024)
  #geom_hline(yintercept=0)+
  #ggtitle(str_wrap("Total consumption loss",40))+
  theme(axis.title = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(#transform="log10",#scales::pseudo_log_trans(base = 10),
                     labels = function(x) sprintf("%g %%", x),
                     #breaks = c(0.0001, 0.01,0.1,1,10),
                     "Capital losses due to local floods")+
  scale_color_manual(values = c( "#DC3220","#005AB5","grey70")) +
  scale_y_continuous(#transform="log",#scales::pseudo_log_trans(base = 10),
                     labels = function(x) sprintf("%g %%", x),
                     #breaks = c(0, 0.5,1,2,3,5,10,15),
                     "Total consumption loss")+
  guides(size = "none")+
  ggtitle("a) Capital losses and total consumption losses")+
  theme_bw(18)+
  theme(plot.title = ggplot2::element_text(family = font, 
        size = 28, face = "bold", color = "#222222"), plot.subtitle = ggplot2::element_text(family = font,
        size = 22, margin = ggplot2::margin(9, 0, 9, 0)), plot.caption = ggplot2::element_blank(),
        legend.position = "top", legend.text.align = 0, legend.background = ggplot2::element_blank(),
        legend.title = ggplot2::element_blank(), legend.key = ggplot2::element_blank(),
        legend.text = ggplot2::element_text(family = font, size = 18,
            color = "#222222"))
  #scale_size_area(max_size = 10)
p

q<- p + facet_zoom(xlim = c(0,1),ylim=c(0,10),zoom.size=0.5,show.area=FALSE)
q


xlim_from <- c(0, 1)
ylim_from <- c(0, 10)
xlim_to <- c(10,17)
ylim_to <- c(0,10)

# Create the zoomed-in plot
zoom_plot <- p +
  xlim(xlim_from) +
  ylim(ylim_from) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    title = element_blank(),
    axis.text = element_text(size = 6),
    plot.background = element_rect(fill = "white", color = "black"),
    legend.position = "none",
  )


q<-p + annotation_custom(
    grob = ggplotGrob(zoom_plot), 
    xmin = xlim_to[1], xmax = xlim_to[2], 
    ymin = ylim_to[1], ymax = ylim_to[2]
  ) +
  annotate("rect", xmin = xlim_from[1], xmax = xlim_from[2], ymin = ylim_from[1], ymax = ylim_from[2], 
           color = "red", fill = NA, linetype = "dashed")
q



from <- c(xmin = 0, xmax = 1, ymin = 0, ymax = 10)
#Names xmin, xmax, ymin, ymax are optional:
to <- c(10, 17,0, 10)
q <- p+ geom_magnify(from = from, to = to,
                  shadow = FALSE)

q<-ggMarginal(p,margins = 'y',groupFill = FALSE,,type = "histogram")
  
#transform = scales::transform_pseudo_log(base = 10)
q

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig3_direct.png"),plot=q,
       width = 2666/300,
       height= 1875/300,
       unit="in")
}

```
## figure 5 (quantiles)
### graph relative
```{r}

tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  mutate(Quartile_risk = cut(constant*10,breaks=quantile(constant*10,probs = 0:4/4), include.lowest = TRUE)) %>% 
  filter(constant>10^-4)


p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_rel ))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  geom_point(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Change in consumption losses when opening trade (%)",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(-0.5, 0.75, 0.25))

q<-ggMarginal(p,margins = 'y',fill="#1380A1",type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```

### graph absolute
```{r}

tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  mutate(Quartile_risk = cut(constant*10,breaks=quantile(constant*10,probs = 0:4/4), include.lowest = TRUE)) %>% 
  filter(constant>10^-4)%>% 
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))


p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_abs ))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  #geom_point(alpha=0.7,fill="#1380A1",color="#1380A1")+
  geom_point(alpha=0.7,aes(fill=`Trade Zone`,color=`Trade Zone`),size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Change in consumption losses when opening trade",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_color_manual(values = c( "#DC3220","#005AB5"))+
  scale_y_continuous(labels = function(x) sprintf("%g %%", x*100),)

q<-ggMarginal(p,margins = 'y',groupFill = TRUE,type = "histogram") 

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only_abs.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```

### graph relative bicolore

#### essai avec titre
```{r}

tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  filter(constant>10^-4)%>% 
    left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))%>% 
  left_join(population, by=c("Country" = "Country Code"))


tmp %>% 
  mutate(sign=if_else(diff_abs>0,"increase losses","decrease losses")) %>% 
  group_by(sign) %>% 
  summarise(number=n(),
            population_billion=round(sum(population_2024,na.rm=TRUE)/1e9,1))


p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_rel,fill=`Trade Zone`,color=`Trade Zone`))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  geom_point(aes(size=population_2024),alpha=0.7)+
  #geom_point(size=3,alpha=0.7)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Change in consumption losses when opening trade (%)",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(-0.5, 0.75, 0.25))+
  scale_color_manual(values = c( "#DC3220","#005AB5"))+
  guides(size = "none")

q<-ggMarginal(p,margins = 'y',groupFill = TRUE,type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only_bicolore.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```

#### essai sans titre (legende)
```{r}

tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  filter(constant>10^-4)%>% 
    left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))%>% 
  left_join(population, by=c("Country" = "Country Code"))


tmp %>% 
  mutate(sign=if_else(diff_abs>0,"increase losses","decrease losses")) %>% 
  group_by(sign) %>% 
  summarise(number=n(),
            population_billion=round(sum(population_2024,na.rm=TRUE)/1e9,1))


p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_rel,fill=`Trade Zone`,color=`Trade Zone`))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  geom_point(aes(size=population_2024),alpha=0.7)+
  #geom_point(size=3,alpha=0.7)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  geom_hline(yintercept=0)+
  bbc_style()+
  #ggtitle(str_wrap("Change in consumption losses when opening trade (%)",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.title.y = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(-0.5, 0.75, 0.25))+
  scale_color_manual(values = c( "#DC3220","#005AB5"))+
  guides(size = "none")+
  labs(y="Change in consumption losses\nwhen opening trade (%)")

q<-ggMarginal(p,margins = 'y',groupFill = TRUE,type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only_bicolore_legend.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```
## figure 7 (quantiles club)
### graph relative
```{r}

tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`,`Trade Zone` )) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(isolation-constant)/constant,
         diff_abs=(isolation-constant)) %>% 
  filter(constant>10^-4) %>% 
    left_join(population, by=c("Country" = "Country Code"))

tmp %>% 
  mutate(sign=if_else(diff_abs>0,"increase losses","decrease losses")) %>% 
  group_by(sign) %>% 
  summarise(number=n(),
            population_billion=round(sum(population_2024,na.rm=TRUE)/1e9,1))


#number of countries with increase
sum(tmp$diff_abs>0)
#number of countries with decrease
sum(tmp$diff_abs<0)

p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_rel,fill=`Trade Zone`,color=`Trade Zone`))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  geom_hline(yintercept=0)+
  geom_point(alpha=0.7,size=3)+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  bbc_style()+
  ggtitle(str_wrap("Change in consumption losses (%) when isolating high risk countries",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(-0.5, 0.75, 0.25))+
  scale_color_manual(values = c( "#DC3220","#005AB5"))


q<-ggMarginal(p,margins = 'y',groupFill = TRUE,type = "histogram")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only_club.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```

### graph absolute
```{r}

tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(isolation-constant)/constant,
         diff_abs=(isolation-constant)) %>% 
  mutate(Quartile_risk = cut(constant*10,breaks=quantile(constant*10,probs = 0:4/4), include.lowest = TRUE)) %>% 
  filter(constant>10^-4)%>% 
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))


p<-tmp %>% 
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=constant,y=diff_abs ))+
  #geom_histogram(binwidth=2,alpha=0.5, position=position_dodge2(preserve = "single",padding = 0.9))+
  #geom_point(alpha=0.7,fill="#1380A1",color="#1380A1")+
  geom_point(alpha=0.7,size=3,aes(fill=`Trade Zone`,color=`Trade Zone`))+
  #geom_boxplot(alpha=0.,outlier.shape = NA)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Change in consumption losses when isolating high risk countries",40))+
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  scale_x_continuous(trans='log10',
                     labels = function(x) sprintf("%g %%", x*100),
                     "Consumption Loss (Central scenario)")+
  scale_color_manual(values = c( "#DC3220","#005AB5"))+
  scale_y_continuous(labels = function(x) sprintf("%g %%", x*100),)

q<-ggMarginal(p,margins = 'y',groupFill = TRUE,type = "histogram") 

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig5_only_abs_club.png"),plot=q,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
q

```
# comparaison cout importé et local


## fraction par pays
```{r}

results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade == "constant") %>% 
  dplyr::select(c(Country, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>%  
  mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Local Consumption loss (%)` = (`Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Foreign Consumption loss (%)` = (`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         ) %>% 
  dplyr::select(-ends_with("($ bn)")) %>% 
  dplyr::select(-ends_with("(bn $)")) %>% 
  mutate(`Fraction of foreign consumption loss` = `Foreign Consumption loss (%)`/`Consumption loss (%)`,
         `Fraction of local consumption loss` = `Local Consumption loss (%)`/`Consumption loss (%)`) %>%
  ggplot(aes(x=`Fraction of foreign consumption loss` ))+
  geom_histogram(binwidth=0.05)
  
  
  
  
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  mutate(Quartile_risk = cut(constant*10,breaks=quantile(constant*10,probs = 0:4/4), include.lowest = TRUE)) %>% 
  filter(constant>10^-4)

dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  ggplot(aes(y=`Consumption loss (%)`,x=`climate`,color=trade))+
  geom_jitter()+
  geom_boxplot()


  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Global consumption losses with low and high trade scenarios (%)",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Global Warming")
```
# histogram unif

## comparison
```{r}
tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  mutate(trade=case_when(
    trade == "low" ~ "Low trade",
    trade == "high" ~ "High trade",
  )) %>% 
  #dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100)  #on divise par 100 pour avoir des %

#probleme, ca calcule la perte de cono finale, et pas de conso totale...
media<-tmp %>% 
  group_by(trade) %>% 
  summarise(`Global consumption loss (%)` = sum(`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`))


p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=`Total Consumption Loss (%)`,fill=trade ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_bar(width = 0.75,position=position_dodge2(preserve = "single")) +
  scale_x_binned(breaks = seq(0, 1, by = 0.02),labels = function(x) sprintf("%g%%", x*100))+
  #geom_density(alpha=0.6)+
  #geom_vline(data=media,aes(xintercept=`Global consumption loss (%)`, color=trade),
  #           linetype="dashed")+
  #geom_density(alpha=.2) +
    geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        #plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0))
        )+
  xlab("Total Consumption Loss (%)")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p
```
## difference absolue
```{r}
tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  #dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>%   #on divise par 100 pour avoir des %
  mutate(percent_loss = cut(`Total Consumption Loss (%)`,
                            breaks=seq(0,max(`Total Consumption Loss (%)`)+0.01,0.01), 
                            include.lowest = TRUE,
                            #labels = sprintf("%g%%", seq(0.01,max(`Total Consumption Loss (%)`)+0.01,0.01)*100)
                            labels = sprintf("%f", seq(0.005,max(`Total Consumption Loss (%)`)+0.005,0.01))
                            )) %>% 
  group_by(trade,percent_loss) %>% 
  summarise(number=n()) %>% 
  pivot_wider(values_from = number,names_from = trade) %>% 
  mutate(low=if_else(is.na(low),0,low)) %>% 
  mutate(high=if_else(is.na(high),0,high)) %>% 
  mutate(variation = high-low)%>% 
  mutate(percent_loss=as.numeric(as.character(percent_loss)))
  
p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=percent_loss,y=variation ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_col() +
  bbc_style()+
    geom_hline(yintercept=0)+
  ggtitle(str_wrap("Number of countries",40),subtitle = "Variation when opening trade")+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"))+
  scale_x_continuous(labels = function(x) sprintf("%g%%", x*100),breaks = seq(0, 0.18, by = 0.02))+
  xlab("Total Consumption Loss (%)")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new_variation.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p
```
## difference relative
```{r}
tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  filter(constant>10^-4) %>% 
    left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))




p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=diff_rel,fill=`Trade Zone`))+ #diff rel ou abs ?
  geom_histogram(binwidth=0.02,color="black" )+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  xlab("Relative effect of trade openness on consumption losses (%)")+
  scale_x_continuous(breaks = seq(-0.5, 1, by = 0.25),labels = function(x) sprintf("%g%%", x*100))+ 
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0,
             linetype="dashed")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new_rel.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}

p
```

## difference absolue 2
```{r}
tmp<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  filter(constant>10^-4) %>% 
    left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))




tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=diff_abs,fill=`Trade Zone`))+ #diff rel ou abs ?
  geom_histogram(binwidth=0.005,color="black" )+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  xlab("Relative effect of trade openness on consumption losses (%)")+
  scale_x_continuous(breaks = seq(-0.5, 1, by = 0.01),labels = function(x) sprintf("%g%%", x*100))+ 
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0,
             linetype="dashed")


```
# histogram club

## comparison
```{r}
tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  mutate(trade=case_when(
    trade == "constant" ~ "constant",
    trade == "isolation" ~ "isolation",
  )) %>% 
  #dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100)  #on divise par 100 pour avoir des %

#probleme, ca calcule la perte de cono finale, et pas de conso totale...
media<-tmp %>% 
  group_by(trade) %>% 
  summarise(`Global consumption loss (%)` = sum(`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`))


p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=`Total Consumption Loss (%)`,fill=trade ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_bar(width = 0.75,position=position_dodge2(preserve = "single")) +
  scale_x_binned(breaks = seq(0, 1, by = 0.02),labels = function(x) sprintf("%g%%", x*100))+
  #geom_density(alpha=0.6)+
  #geom_vline(data=media,aes(xintercept=`Global consumption loss (%)`, color=trade),
  #           linetype="dashed")+
  #geom_density(alpha=.2) +
    geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        #plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0))
        )+
  xlab("Total Consumption Loss (%)")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new_club.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p
```
## difference absolue
```{r}
tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  mutate(trade=case_when(
    trade == "constant" ~ "constant",
    trade == "isolation" ~ "isolation",
  )) %>% 
  #dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>%   #on divise par 100 pour avoir des %
  mutate(percent_loss = cut(`Total Consumption Loss (%)`,
                            breaks=seq(0,max(`Total Consumption Loss (%)`)+0.01,0.01), 
                            include.lowest = TRUE,
                            #labels = sprintf("%g%%", seq(0.01,max(`Total Consumption Loss (%)`)+0.01,0.01)*100)
                            labels = sprintf("%f", seq(0.005,max(`Total Consumption Loss (%)`)+0.005,0.01))
                            )) %>% 
  group_by(trade,percent_loss,`Trade Zone`) %>% 
  summarise(number=n()) %>% 
  pivot_wider(values_from = number,names_from = trade) %>% 
  mutate(constant=if_else(is.na(constant),0,constant)) %>% 
  mutate(isolation=if_else(is.na(isolation),0,isolation)) %>% 
  mutate(variation = isolation-constant)%>% 
  mutate(percent_loss=as.numeric(as.character(percent_loss)))
  
p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=percent_loss,y=variation,fill = `Trade Zone` ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_col() +
  bbc_style()+
    geom_hline(yintercept=0)+
  ggtitle(str_wrap("Number of countries",40),subtitle = "Variation when opening trade within club")+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"))+
  scale_x_continuous(labels = function(x) sprintf("%g%%", x*100),breaks = seq(0, 0.18, by = 0.02))+
  xlab("Total Consumption Loss (%)")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new_variation_club.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p
```
## difference relative
```{r}
tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`,`Trade Zone` )) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(isolation-constant)/constant,
         diff_abs=(isolation-constant)) %>% 
  filter(constant>10^-4)




p<-tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=diff_rel,fill=`Trade Zone`))+ #diff rel ou abs ?
  geom_histogram(binwidth=0.02,color="black" )+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  xlab(str_wrap("Change in consumption losses (%) when isolating high risk countries",40))+
  scale_x_continuous(breaks = seq(-0.5, 1, by = 0.25),labels = function(x) sprintf("%g%%", x*100))+ 
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0,
             linetype="dashed")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig_histo_new_rel_club.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p
```
## difference absolue 2
```{r}
tmp<-results_club %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`,`Trade Zone` )) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(isolation-constant)/constant,
         diff_abs=(isolation-constant)) %>% 
  filter(constant>10^-4)




tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=diff_abs,fill=`Trade Zone`))+ #diff rel ou abs ?
  geom_histogram(binwidth=0.005,color="black" )+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  xlab(str_wrap("Change in consumption losses when isolating high risk countries",40))+
  scale_x_continuous(breaks = seq(-1, 1, by = 0.01),labels = function(x) sprintf("%g%%", x*100))+ 
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0,
             linetype="dashed")


```

# global warming

## aggregated
```{r}
p<-results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Global consumption loss (%)` = sum(`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  ggplot(aes(y=`Global consumption loss (%)`,x=`climate`,fill=trade))+
  geom_col(position = position_dodge())+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Global consumption losses with low and high trade scenarios (%)",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Global Warming")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p

```
## aggregated club
```{r}
p<-results2_club %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Global consumption loss (%)` = sum(`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  ggplot(aes(y=`Global consumption loss (%)`,x=`climate`,fill=trade))+
  geom_col(position = position_dodge())+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Global consumption losses with low and high trade scenarios (%)",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Global Warming")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_club.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p

```

## aggregated foreign local
```{r}
p <- results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))%>% 
  pivot_longer(cols=c(`Local consumption loss (%)`,`Foreign consumption loss (%)`),
               names_to = "type",values_to = "value") %>%
  ggplot(aes(y=value,x=trade,fill=type))+ #interaction(`climate`,trade)
  geom_col(position = position_stack())+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle("Global consumption losses in different climate scenarios")+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Trade scenario")+
  geom_label(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5,fill="white",alpha=0.5)+
  #geom_shadowtext(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),bg.colour='white',colour="black",size=5)+
  facet_wrap(~climate)


  #ggrepel::geom_text_repel(size = 4, direction = "y", nudge_x = -.5,fill="white")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_foreign_local.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}

p

```
### per country

```{r}

tmp<-results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(climate,Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
    mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(high=(high-constant)/constant,
         low=(low-constant)/constant,
         constant=0) %>% 
#  filter(constant>10^-4) %>% 
  pivot_longer(cols=c("low","high","constant"),values_to = "Consumption loss (%)",names_to = "trade") %>% 
#     left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))
# 
# results2 %>% 
#   filter(climate %in% c(2020, 2050, 2100),
#          future == 2050,
#          SSP == "SSP2",
#          trade %in% c("low","high")) %>% 
#   dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
#   group_by(climate,trade) %>% 
#   mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`)) %>% 
#   mutate(climate=case_when(
#     climate == 2020 ~ "+1.1°C",
#     climate == 2050 ~ "+2.4°C",
#     climate == 2100 ~ "+4.3°C",
#   )) %>% 
#   filter(`Consumption loss (%)`>10^-3)%>% #to remove false point 
  ggplot(aes(y=`Consumption loss (%)`,x=trade))+ #interaction(`climate`,trade)
  geom_jitter(alpha=0.7,fill="#1380A1",color="#1380A1",size=3)+
  geom_boxplot(outlier.shape = NA, alpha=0.5)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle("Global consumption losses in different climate scenarios")+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                      #transform="log10"
                     )+
  xlab("Trade scenario")+
  #geom_text(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5)+
  #geom_shadowtext(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),bg.colour='white',colour="black",size=5)+
  facet_wrap(~climate)


  #ggrepel::geom_text_repel(size = 4, direction = "y", nudge_x = -.5,fill="white")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_foreign_local.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}

p

```

## aggregated club foreign local
### essai 1
```{r}
tmp_non_club <- results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))%>% 
  pivot_longer(cols=c(`Local consumption loss (%)`,`Foreign consumption loss (%)`),
               names_to = "type",values_to = "value")

tmp<-results2_club %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))%>% 
  pivot_longer(cols=c(`Local consumption loss (%)`,`Foreign consumption loss (%)`),
               names_to = "type",values_to = "value") %>% 
  #filter(trade!="constant") %>% 
  rbind(tmp_non_club) %>% 
  mutate(trade=factor(trade,levels=c("low","high","constant","isolation"))) %>% 
  mutate(x=case_when(
    trade =="low" ~ 1,
    trade =="high" ~ 2,
    trade =="constant" ~ 3.5,
    trade =="isolation" ~ 4.5,
  ))

p<- tmp %>%
  ggplot(aes(y=value,x=x,fill=type))+ #interaction(`climate`,trade)
  geom_col(position = position_stack())+
    scale_x_continuous(
    breaks = tmp$x,
    labels = tmp$trade
  ) +
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle("Global consumption losses in different climate scenarios")+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Trade scenario")+
  geom_label(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5,fill="white",alpha=0.5)+
  #geom_text(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5)+
  #geom_shadowtext(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),bg.colour='white',colour="black",size=5)+
  facet_wrap(~climate)


  #ggrepel::geom_text_repel(size = 4, direction = "y", nudge_x = -.5,fill="white")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_club_foreign_local.png"),plot=p,
       width = 2666/350*2,
       height= 1875/350,
       unit="in")
}

p

```

### essai 2a
```{r}
tmp_non_club <- results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","constant","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))%>% 
  pivot_longer(cols=c(`Local consumption loss (%)`,`Foreign consumption loss (%)`),
               names_to = "type",values_to = "value") 

tmp_non_club <- results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","constant","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Consumption Loss ($ bn)` = sum(`Consumption Loss ($ bn)`),
           `Foreign Consumption Loss ($ bn)` =  sum(`Foreign Consumption Loss ($ bn)`),
            `Final consumption (bn $)`= sum(`Final consumption (bn $)`)
            ) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))





p<- tmp_non_club %>%
  ggplot(aes(y=value,x=trade,fill=type))+ #interaction(`climate`,trade)
  geom_col(position = position_stack())+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle("Global consumption losses in different climate scenarios")+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent)+
  xlab("Trade scenario")+
  geom_label(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5,fill="white",alpha=0.5)+
  #geom_text(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5)+
  #geom_shadowtext(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),bg.colour='white',colour="black",size=5)+
  facet_wrap(~climate)


  #ggrepel::geom_text_repel(size = 4, direction = "y", nudge_x = -.5,fill="white")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_club_foreign_local2a.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}

p

```

### essai 2b
```{r}

tmp<-results2_club %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  summarise(`Local consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  ))%>% 
  pivot_longer(cols=c(`Local consumption loss (%)`,`Foreign consumption loss (%)`),
               names_to = "type",values_to = "value") 

p<- tmp %>%
  ggplot(aes(y=value,x=trade,fill=type))+ #interaction(`climate`,trade)
  geom_col(position = position_stack())+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle("Global consumption losses in different climate scenarios")+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent)+
  xlab("Trade scenario")+
  geom_label(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5,fill="white",alpha=0.5)+
  #geom_text(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),size=5)+
  #geom_shadowtext(aes(label = paste0(round(value*10000)/100," %"),group=type),position = position_stack(vjust = .5),bg.colour='white',colour="black",size=5)+
  facet_grid(~climate)


  #ggrepel::geom_text_repel(size = 4, direction = "y", nudge_x = -.5,fill="white")


if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6_club_foreign_local2b.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}

p

```
## facet

```{r}
results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  dplyr::select(c(Country, climate,SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  ungroup() %>% 
  group_by(climate,trade) %>% 
  summarise(`Total Consumption loss (%)` = sum(`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Local Consumption loss (%)` = sum(`Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`),
            `Foreign Consumption loss (%)` = sum(`Foreign Consumption Loss ($ bn)`)/sum(`Final consumption (bn $)`)) %>% 
  dplyr::select(-ends_with("($ bn)")) %>% 
  dplyr::select(-ends_with("(bn $)")) %>% 
  pivot_longer(cols=c(`Total Consumption loss (%)`,`Local Consumption loss (%)`,`Foreign Consumption loss (%)`),
               names_to = "type",values_to = "value")%>% 
  ggplot(aes(y=value,x=trade ))+
  facet_grid(type~climate)+#scales="free_y"
  geom_col()
```

## comparaison importe et local par pays
```{r}

results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  dplyr::select(c(Country, climate,SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>%  
  mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Local Consumption loss (%)` = (`Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Foreign Consumption loss (%)` = (`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         ) %>% 
  filter(`Consumption loss (%)`>10^-4)%>% 
  dplyr::select(-ends_with("($ bn)")) %>% 
  dplyr::select(-ends_with("(bn $)")) %>% 
  pivot_longer(cols=c(`Consumption loss (%)`,`Local Consumption loss (%)`,`Foreign Consumption loss (%)`),
               names_to = "type",values_to = "value") %>% 
  ggplot(aes(y=value,x=trade,color=trade,fill=trade ))+
  facet_grid(type~climate,scales="free")+
  geom_jitter(size=1,alpha=0.7)+
  #geom_point(size=3,alpha=0.7)+
  geom_boxplot(alpha=0.,outlier.shape = NA,colour = "#333333")+
  geom_hline(yintercept=0)+
  bbc_style()+
  #ggtitle(str_wrap("Global consumption losses with low and high trade scenarios (%)",40))+#subtitle = "SSP2"
  scale_color_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(#trans='log10',
                     labels = function(x) sprintf("%g %%", x*100))
 
```
## comparaison hisogramme pays

```{r}
tmp<-results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  dplyr::select(c(Country, climate,SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>%  
  mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Local Consumption loss (%)` = (`Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         `Foreign Consumption loss (%)` = (`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         ) %>% 
  filter(`Consumption loss (%)`>10^-4)%>% 
  dplyr::select(-ends_with("($ bn)")) %>% 
  dplyr::select(-ends_with("(bn $)")) %>% 
  pivot_longer(cols=c(`Consumption loss (%)`,`Local Consumption loss (%)`,`Foreign Consumption loss (%)`),
               names_to = "type",values_to = "value")


p<- tmp %>%   
  mutate(value=if_else(value>0.2,0.2,value)) %>% #on met une limite à 20%
  filter(type == "Consumption loss (%)") %>%
  ggplot(aes(x=value,fill=trade ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_bar(width = 0.75,position=position_dodge2(preserve = "single")) +
  scale_x_binned(breaks = seq(0, 0.2, by = 0.01),labels = function(x) sprintf("%g%%", x*100))+ #,trans='log10'
  facet_grid(climate~type)+
  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        #plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0))
        )+
  xlab("Total Consumption Loss (%)")
  
p

```
## difference histogramme pays

```{r}
tmp<-results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  dplyr::select(c(Country, climate,SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>%  
  mutate(`Total Consumption Loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`),
         ) %>% 
  mutate(`Total Consumption Loss (%)`=if_else(`Total Consumption Loss (%)`>0.2,0.2,`Total Consumption Loss (%)`)) %>% #on met une limite à 20%
  mutate(percent_loss = cut(`Total Consumption Loss (%)`,
                            breaks=seq(0,max(`Total Consumption Loss (%)`)+0.01,0.01), 
                            include.lowest = TRUE,
                            #labels = sprintf("%g%%", seq(0.01,max(`Total Consumption Loss (%)`)+0.01,0.01)*100)
                            labels = sprintf("%f", seq(0.005,max(`Total Consumption Loss (%)`)+0.005,0.01))
                            ))%>% 
  group_by(trade,climate,percent_loss) %>% 
  summarise(number=n()) %>% 
  pivot_wider(values_from = number,names_from = trade) %>% 
  mutate(low=if_else(is.na(low),0,low)) %>% 
  mutate(high=if_else(is.na(high),0,high)) %>% 
  mutate(variation = high-low)%>% 
  mutate(percent_loss=as.numeric(as.character(percent_loss)))

tmp %>%   
#pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  ggplot(aes(x=percent_loss,y=variation ))+
  #geom_histogram(position="dodge",alpha=0.5,preserve = "single",binwidth=0.05)+
  geom_col() +
  bbc_style()+
  geom_hline(yintercept=0)+
  facet_wrap(~climate)+
  ggtitle(str_wrap("Number of countries",40),subtitle = "Variation when opening trade (limite à 20%)")+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"))+
  scale_x_continuous(labels = function(x) sprintf("%g%%", x*100),breaks = seq(0, 0.18, by = 0.02))+
  xlab("Total Consumption Loss (%)")
  

```
## per country
```{r}
results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high")) %>% 
  dplyr::select(c(Country,climate, SSP, trade,`Consumption Loss ($ bn)`,`Foreign Consumption Loss ($ bn)`,`Final consumption (bn $)`)) %>% 
  group_by(climate,trade) %>% 
  mutate(`Consumption loss (%)` = (`Consumption Loss ($ bn)`+`Foreign Consumption Loss ($ bn)`)/(`Final consumption (bn $)`)) %>% 
  mutate(climate=case_when(
    climate == 2020 ~ "+1.1°C",
    climate == 2050 ~ "+2.4°C",
    climate == 2100 ~ "+4.3°C",
  )) %>% 
  ggplot(aes(y=`Consumption loss (%)`,x=`climate`,color=trade))+
  geom_jitter()


  geom_hline(yintercept=0)+
  bbc_style()+
  ggtitle(str_wrap("Global consumption losses with low and high trade scenarios (%)",40))+#subtitle = "SSP2"
  scale_fill_manual(values = c("#FAAB18", "#1380A1")) +
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
   scale_y_continuous(labels = scales::percent,
                     )+
  xlab("Global Warming")

if (SAVE_ici) {
ggsave(paste0("./Figures/Fig6.png"),plot=p,
       width = 2666/350,
       height= 1875/350,
       unit="in")
}
p

```

## graphe en fonctio du niveau initial oer country

```{r}
tmp<-results2 %>% 
  filter(climate %in% c(2020, 2050, 2100),
         future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,climate,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  filter(constant>10^-4)%>% 
    left_join(gdp_riskiest_aggregation,by= c("Country" = "Code"))%>% 
  left_join(population, by=c("Country" = "Country Code"))


tmp %>% 
  mutate(sign=if_else(diff_abs>0,"increase losses","decrease losses")) %>% 
  group_by(sign,climate) %>% 
  summarise(number=n(),
            population_billion=round(sum(population_2024,na.rm=TRUE)/1e9,1))



p<-tmp %>% 
    ggplot(aes(x=diff_rel,fill=`Trade Zone`))+ #diff rel ou abs ?
  geom_histogram(binwidth=0.02,color="black" )+
  bbc_style()+
  ggtitle(str_wrap("Number of countries",40))+#subtitle = "SSP2"
  theme(axis.title.x = ggplot2::element_text(family = "Helvetica", size = 18,color = "#222222"),
        axis.ticks.x = element_line(colour = "#333333"), 
        axis.ticks.length =  unit(0.26, "cm"),
        plot.title = ggplot2::element_text(family = "Helvetica",size = 18, margin = ggplot2::margin(9, 0, 9, 0)))+
  xlab("Relative effect of trade openness on consumption losses (%)")+
  scale_x_continuous(breaks = seq(-0.5, 1, by = 0.25),labels = function(x) sprintf("%g%%", x*100))+ 
  geom_hline(yintercept=0)+
  geom_vline(xintercept=0,
             linetype="dashed")+
  facet_wrap(~climate)

p


```

# map

## capital losses absolute
```{r}

countries<-read_excel("country_codes_2.xlsx")

map_results<-results %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Capital Damage ($ bn)`,`Capital (bn $)`)) %>% 
  mutate(`Capital Loss (%)` = `Capital Damage ($ bn)`/`Capital (bn $)`*100) %>% #on divise par 100 pour avoir des %
  left_join(countries,by= join_by('Country' == 'Country Code')) 
  #rename(value=diff_rel) %>% 
  #mutate(value=if_else(value>=1.2,1.2,value))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")

# worldUN <- read_sf(dsn="./TM_WORLD_BORDERS-0.3/",layer="TM_WORLD_BORDERS-0.3")
# worldUN<- read_sf(dsn="./World_Bank/",layer="WB_GAD_ADM0")
# mybreaks=c(0,0.02,0.03,0.04,0.05,0.1,0.2,1)*100
#   mutate(value = cut(value*100, 
#                      breaks =mybreaks,
#                      include.lowest=TRUE,
#                      #labels = c(""),
#                      right=TRUE
#   )) 

map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=`Capital Loss (%)`/100), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    ggtitle("a) Annualized capital losses (2045-2055)")+
  scale_fill_viridis(direction=-1,option="inferno",labels = scales::label_percent(),limits=c(0.,0.2))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        #legend.position = "right",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        legend.position = c(0.12, 0.3))+
  labs(fill="")
  

plot(world_results)
ggsave(paste0("./Figures/map_countries_capital_damage.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")



```
## map total loss
```{r}

countries<-read_excel("country_codes_2.xlsx")

map_results<-results %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  left_join(countries,by= join_by('Country' == 'Country Code')) 
  #rename(value=diff_rel) %>% 
  #mutate(value=if_else(value>=1.2,1.2,value))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")

# worldUN <- read_sf(dsn="./TM_WORLD_BORDERS-0.3/",layer="TM_WORLD_BORDERS-0.3")
# worldUN<- read_sf(dsn="./World_Bank/",layer="WB_GAD_ADM0")
# mybreaks=c(0,0.02,0.03,0.04,0.05,0.1,0.2,1)*100
#   mutate(value = cut(value*100, 
#                      breaks =mybreaks,
#                      include.lowest=TRUE,
#                      #labels = c(""),
#                      right=TRUE
#   )) 

map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=`Total Consumption Loss (%)`), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    ggtitle("b) Consumption losses (2045-2055)")+
  scale_fill_viridis(direction=-1,option="inferno",labels = scales::label_percent(),limits=c(0.,0.2))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        #legend.position = "right",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        legend.position = c(0.12, 0.3))+
  labs(fill="")
  

plot(world_results)
ggsave(paste0("./Figures/map_countries_total_losses.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")



```

## high et low risk
```{r}

countries<-read_excel("country_codes_2.xlsx")

map_results<-results %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Capital Damage ($ bn)`,`Capital (bn $)`)) %>% 
  mutate(`Capital Loss (%)` = `Capital Damage ($ bn)`/`Capital (bn $)`*100) %>% #on divise par 100 pour avoir des %
  left_join(gdp_riskiest_aggregation,by= c("Country" = "Code")) %>% 
      mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>%
    left_join(countries,by= join_by('Country' == 'Country Code')) %>% 
  filter(!is.na(number))
  #rename(value=diff_rel) %>% 
  #mutate(value=if_else(value>=1.2,1.2,value))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")

# worldUN <- read_sf(dsn="./TM_WORLD_BORDERS-0.3/",layer="TM_WORLD_BORDERS-0.3")
# worldUN<- read_sf(dsn="./World_Bank/",layer="WB_GAD_ADM0")
# mybreaks=c(0,0.02,0.03,0.04,0.05,0.1,0.2,1)*100
#   mutate(value = cut(value*100, 
#                      breaks =mybreaks,
#                      include.lowest=TRUE,
#                      #labels = c(""),
#                      right=TRUE
#   )) 

map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=`Trade Zone`),alpha=0.7, lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    ggtitle("b) Distribution of countries into low, and high flood groups")+
  scale_fill_manual(values = c( "#DC3220","#005AB5"),na.translate = F) +
  #scale_fill_viridis(direction=-1,option="inferno",labels = scales::label_percent(),limits=c(0.,0.1))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        #legend.position = "right",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        legend.position = c(0.12, 0.3))+
  labs(fill="")
  

plot(world_results)
ggsave(paste0("./Figures/map_low_high.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")
```
## map relative impact trade openness

### essai 1 (titre, pas legende)
```{r}

countries<-read_excel("country_codes_2.xlsx")


map_results<-results %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  left_join(countries,by= join_by('Country' == 'Country Code')) %>% 
  rename(value=diff_rel) %>% 
  mutate(value=if_else(value>=1.2,1.2,value)) %>% 
  mutate(diff_abs = cut(diff_abs,
                            breaks = c(-1,-0.06,-0.04,-0.02,0,0.02),
                            include.lowest = TRUE,
                            labels = c("< -6%", "[-6% , -4%)", "[-4% , -2%)", "[-2% , 0%)","[0% , +2%)")))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")


map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=value), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    ggtitle("Change in consumption losses when opening trade")+#,subtitle= "from “Low trade” to “High trade” scenario\n2050 SSP2 and 2045-2055 warming level" )+
  scale_fill_distiller(palette="RdBu",
                        limits = c(-1, 1),
                        labels = scales::percent,
                        direction=-1)+
  # scale_fill_gradientn(colours=brewer.pal(7,"YlGn"))+
  #scale_fill_viridis(direction=1)+
    #labs(fill = "Cross-border\nclimate exposure (%)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        #legend.position = "right",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        legend.position = c(0.12, 0.3))+
  labs(fill="")


plot(world_results)
ggsave(paste0("./Figures/map_countries_rel_change_openness.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")




```

### essai 2 (legende en haut)
```{r}

countries<-read_excel("country_codes_2.xlsx")


map_results<-results %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  left_join(countries,by= join_by('Country' == 'Country Code')) %>% 
  rename(value=diff_rel) %>% 
  mutate(value=if_else(value>=1.2,1.2,value)) %>% 
  mutate(diff_abs = cut(diff_abs,
                            breaks = c(-1,-0.06,-0.04,-0.02,0,0.02),
                            include.lowest = TRUE,
                            labels = c("< -6%", "[-6% , -4%)", "[-4% , -2%)", "[-2% , 0%)","[0% , +2%)")))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")


map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=value), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    #ggtitle("Change in consumption losses when opening trade")+#,subtitle= "from “Low trade” to “High trade” scenario\n2050 SSP2 and 2045-2055 warming level" )+
  scale_fill_distiller(palette="PuOr",
                        limits = c(-1, 1),
                        labels = scales::percent,
                        direction=-1)+
  # scale_fill_gradientn(colours=brewer.pal(7,"YlGn"))+
  #scale_fill_viridis(direction=1)+
    #labs(fill = "Cross-border\nclimate exposure (%)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.position = "top",
        legend.direction = "horizontal",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        #legend.position = c(0.12, 0.3)
        )+
    guides(
    fill = guide_colorbar(
      title.position = "top",   # title above the bar
      title.hjust = 0.5,         # center the title (optional)
      barwidth = unit(0.9, "npc"),   # key trick: relative width
      barheight = unit(0.5, "cm"),
    ))+
  labs(fill="Change in consumption losses when opening trade")


plot(world_results)
ggsave(paste0("./Figures/map_countries_rel_change_openness_legend.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")




```

## map club relative impact trade openness
### essai 2 (legende en haut)
```{r}

countries<-read_excel("country_codes_2.xlsx")


map_results<-results_club %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("constant","isolation")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(isolation-constant)/constant,
         diff_abs=(isolation-constant)) %>% 
  left_join(countries,by= join_by('Country' == 'Country Code')) %>% 
  rename(value=diff_rel) %>% 
  mutate(value=if_else(value>=1.2,1.2,value)) %>% 
  mutate(diff_abs = cut(diff_abs,
                            breaks = c(-1,-0.06,-0.04,-0.02,0,0.02),
                            include.lowest = TRUE,
                            labels = c("< -6%", "[-6% , -4%)", "[-4% , -2%)", "[-2% , 0%)","[0% , +2%)")))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")


map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=value), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    #ggtitle("Change in consumption losses when opening trade")+#,subtitle= "from “Low trade” to “High trade” scenario\n2050 SSP2 and 2045-2055 warming level" )+
  scale_fill_distiller(palette="PuOr",
                        limits = c(-1, 1),
                        labels = scales::percent,
                        direction=-1)+
  # scale_fill_gradientn(colours=brewer.pal(7,"YlGn"))+
  #scale_fill_viridis(direction=1)+
    #labs(fill = "Cross-border\nclimate exposure (%)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.position = "top",
        legend.direction = "horizontal",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        #legend.position = c(0.12, 0.3)
        )+
    guides(
    fill = guide_colorbar(
      title.position = "top",   # title above the bar
      title.hjust = 0.5,         # center the title (optional)
      barwidth = unit(0.9, "npc"),   # key trick: relative width
      barheight = unit(0.5, "cm"),
    ))+
  labs(fill="Change in consumption losses when reducing\ntrade with high risk countries")


plot(world_results)
ggsave(paste0("./Figures/map_countries_rel_change_club_legend.png"),
       plot=world_results,
      width = 1875/300*21/11,
       height= 1875/300,
       unit="in")




```
## map absolute impact of trade openness 
```{r}

countries<-read_excel("country_codes_2.xlsx")


map_results<-results %>% 
    mutate(`Country`=case_when(
    `Country` == "SDS" ~"SSD",
    `Country` == "SUD" ~"SDN",
    TRUE ~ `Country`
  )) %>% 
  filter(future == 2050,
         SSP == "SSP2",
         trade %in% c("low","high","constant")) %>% 
  dplyr::select(c(Country,future, SSP, trade,`Total Consumption Loss (%)`)) %>% 
  mutate(`Total Consumption Loss (%)` = `Total Consumption Loss (%)`/100) %>% #on divise par 100 pour avoir des %
  pivot_wider(names_from = trade,values_from = `Total Consumption Loss (%)`) %>% 
  mutate(diff_rel=(high-low)/low,
         diff_abs=(high-low)) %>% 
  left_join(countries,by= join_by('Country' == 'Country Code')) %>% 
  rename(value=diff_rel) %>% 
  mutate(value=if_else(value>=1.2,1.2,value)) %>% 
  mutate(diff_abs = cut(diff_abs,
                            breaks = c(-1,-0.06,-0.04,-0.02,0,0.02),
                            include.lowest = TRUE,
                            labels = c("< -6%", "[-6% , -4%)", "[-4% , -2%)", "[-2% , 0%)","[0% , +2%)")))

world <- ne_countries(scale='medium', returnclass="sf", type = "countries")


map_results2<-map_results %>% 
  left_join(world,.,by=c("iso_a3_eh" = "Country" )) 

world_results<-ggplot(data=world) + 
    #geom_sf(fill = "grey90", lwd=0.05) + 
    geom_sf(data=map_results2 , aes(fill=diff_abs), lwd=0.3)+
    coord_sf(ylim = c(-65,90), expand = FALSE) + #World
    #coord_sf(ylim = c(30,65), xlim = c(-15,40), expand = FALSE) + #Europe
    #coord_sf(ylim = c(20,50), xlim = c(-125,-65), expand = FALSE) + #USA
    #coord_sf(ylim = c(-40,-5), xlim = c(110,155), expand = FALSE) + #Australia
    xlab('') + ylab('') +
    theme(panel.background = element_rect(fill = "white"),#"aliceblue"
          plot.margin=unit(c(0,0,0,0),"mm"))+
    ggtitle(paste0(""), 
            )+
  scale_fill_manual(values = c( #RColorBrewer::brewer.pal(6, "RdBu")
"#B2182B", "#EF8A62", "#FDDBC7", "#D1E5F0", "#67A9CF", "#2166AC"
  )
  )+
  # scale_fill_gradientn(colours=brewer.pal(7,"YlGn"))+
  #scale_fill_viridis(direction=1)+
    labs(fill = "Cross-border\nclimate exposure (%)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        #legend.position = "right",
        legend.title = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        legend.text = ggplot2::element_text(family = font, size = 22, color = "#222222"),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        plot.title = ggplot2::element_text(family = font, size = 28, face = "bold", color = "#222222"), 
        plot.subtitle = ggplot2::element_text(family = font, size = 22, margin = ggplot2::margin(9, 0, 9, 0)),
        legend.position = c(0.12, 0.3))+
  labs(fill="")


plot(world_results)
ggsave(paste0("./Figures/countries.png"),plot=world_results,width = 27, height = 11, units = "cm",device = "png",dpi = 200)




```
# map arrows

## Indirect impacts : losses propagation

```{r}

#| fig.width: 1300px


coord1<-fond_carte %>% st_centroid() %>% st_coordinates() %>% as.data.frame()
coord2<-fond_carte %>% st_drop_geometry()  %>% bind_cols(coord1) %>% 
  rename(longitude='X',latitude='Y') %>% 
  group_by(CONTINENT) %>% 
  mutate(longitude=sum(longitude*POP_EST,na.rm=TRUE)/sum(POP_EST),
            latitude=sum(latitude*POP_EST,na.rm=TRUE)/sum(POP_EST))

OD <- drias_agreg_by_model %>% 
  filter(SELF_damage=='OTHER',
         MRIO=='exiobase3_2020_74_sectors',
         period=='Historical period 1970-2015',
         #model=='r1'
         ) %>% 
  dplyr::select(c(region_flooded,region_output,total_f)) %>% 
  left_join(coord2,by = c("region_flooded"="EXIO3_id")) %>% 
  left_join(coord2,by = c("region_output"="EXIO3_id")) %>% 
  group_by(CONTINENT.x,latitude.x,longitude.x,CONTINENT.y,latitude.y,longitude.y) %>% 
  summarise(total_f=sum(total_f)) %>% 
  filter(CONTINENT.x!=CONTINENT.y) 

#world <- ne_countries(scale = "medium", returnclass = "sf")
world_map<-
 ggplot(data = OD) + 
  vincent_style()+
  #geom_sf(data =fond_carte , alpha = 0.2) + # Ajout d
   geom_sf(data= fond_carte)+
  coord_sf(ylim = c(-65,90), expand = FALSE)+
  xlab('') + ylab('') +
 labs(subtitle = "")+
     ggtitle(paste0(""))+
  theme(legend.position = "right",
                plot.title = element_blank(),
        plot.subtitle = element_blank())+
  geom_curve(aes(x = longitude.x, 
                 y = latitude.x, 
                 xend = longitude.y,
                 yend = latitude.y,
                 size=total_f,
                 color=CONTINENT.y),
             lineend='butt',
             linejoin='butt',
             curvature = -0.3, 
             arrow = arrow(length = unit(0.06, "npc")),
             alpha=0.8,
             ) +
  scale_size_continuous(range = c(1,10),trans="identity")+
  facet_wrap('CONTINENT.x')+
  guides(size=guide_legend(title="Exported consumption\nlosses"))+
  guides(color=guide_legend(title="Towards", override.aes=list(linewidth=4), ncol = 2))+
  theme(legend.title = element_text(size = 16), legend.text = element_text(size=14))  

  
plot(world_map,
      width = 27, 
      height = 11, 
      units = "cm")
     #width = 27, hei
```



